---
title: "05_ControlModels"
output: pdf_document
date: "2025-07-31"
editor_options: 
  chunk_output_type: console
---

# Dataset with Only Non-Overlapping Leave

## Home Time Percentage

```{r}
formula_zoib <- bf(
  totalHomeTimePercent_01 ~ 0 + Role + Role:Leave + Leave:mo(d_epdst_sum) + Leave:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality) + (Leave | gr(ParticipantID, by = Role)),
  zoi ~ 0 + Role + Role:Leave + Leave:mo(d_epdst_sum) + Leave:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality),
  coi ~ 0 + Role + Role:Leave + Leave:mo(d_epdst_sum) + Leave:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality),
  phi ~ 0 + Role + Role:Leave
)

priors_zoib <- c(
  # Main regression (mu)
  prior(normal(0, 3), class = b),
  prior(normal(0, 3), class = b, dpar = "zoi"),
  prior(normal(0, 3), class = b, dpar = "coi"),
  prior(normal(0, 2), class = b, dpar = "phi"),
  prior(normal(0, 2), class = sd, group = ParticipantID),
  prior(lkj(2), class = cor, group = ParticipantID)
)

modelHomeTimePercent_nonoverlapping <- brm(
    formula_zoib,
    prior = priors_zoib,
    family = zero_one_inflated_beta(),
    data = filter(d_GPS_nonoverlap, isWeekend == "Weekday"),
    init = 0,
    cores = 64,
    chains = 2,
    warmup = 500,
    iter = 2000,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    backend = 'cmdstan')

pp_check(modelHomeTimePercent_nonoverlapping, ndraws = 100)
```

## maxDistanceFromHomeKm
```{r}
formula_1 <- bf(
  maxDistanceFromHomeKm ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality) + (Leave | gr(ParticipantID, by = Role)),
  hu ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality),
  shape ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality)
)

priors_hurdle <- c(
  # Main effects for Role (intercepts)
  prior(normal(2, 1), class = b, coef = "RoleFather"),
  prior(normal(2, 1), class = b, coef = "RoleMother"),
  
  # Priors for other interactions
  prior(normal(0, 0.3), class = b),
  
  # Hurdle part (hu) - probability of having any distance
  prior(normal(-1, 0.5), class = b, coef = "RoleFather", dpar = "hu"),
  prior(normal(-1, 0.5), class = b, coef = "RoleMother", dpar = "hu"),
  prior(normal(0, 0.3), class = b, dpar = "hu"),
  
  # Sigma part - controls variability
  prior(normal(1, 0.5), class = b, coef = "RoleFather", dpar = "shape"),
  prior(normal(1, 0.5), class = b, coef = "RoleMother", dpar = "shape"),
  prior(normal(0, 0.3), class = b, dpar = "shape"),
  
  # Random effects
  prior(exponential(2), class = sd),
  prior(lkj(2), class = cor)
)

modelmaxdistance_nonoverlapping <- brm(
    formula_1,
    family = hurdle_gamma(),
    prior = priors_hurdle,
    data = filter(d_GPS_nonoverlap, isWeekend == "Weekday"),
    cores = 64,
    chains = 2,
    warmup = 500,
    iter = 2000,
    control = list(adapt_delta = 0.9, max_treedepth = 15),
    backend = 'cmdstan')
```

## Location Variance
```{r}
formula_1 <- bf(
  locationVariance ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality) + (Leave | gr(ParticipantID, by = Role)),
  hu ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality),
  shape ~ 0 + Role + Role:Leave + Role:mo(d_epdst_sum) + Role:mo(SleepQuality) + Role:Leave:mo(d_epdst_sum) + Role:Leave:mo(SleepQuality)
)

priors_hurdle <- c(
  # Main effects for Role (intercepts)
  prior(normal(2, 2), class = b, coef = "RoleFather"),
  prior(normal(2, 2), class = b, coef = "RoleMother"),
  
  # Role:Leave interactions:
  prior(normal(0, 0.5), class = b, coef = "RoleFather:LeavePaternityLeave"),
  prior(normal(0, 0.5), class = b, coef = "RoleMother:LeavePaternityLeave"),
  
  # Priors for other interactions
  prior(normal(0, 0.3), class = b),
  
  # Hurdle part (hu) - probability of having any distance
  prior(normal(-1, 0.5), class = b, coef = "RoleFather", dpar = "hu"),
  prior(normal(-1, 0.5), class = b, coef = "RoleMother", dpar = "hu"),
  prior(normal(0, 0.3), class = b, dpar = "hu"),
  
  # Sigma part - controls variability
  prior(normal(1, 0.5), class = b, coef = "RoleFather", dpar = "shape"),
  prior(normal(1, 0.5), class = b, coef = "RoleMother", dpar = "shape"),
  prior(normal(0, 0.3), class = b, dpar = "shape"),
  
  # Random effects
  prior(exponential(2), class = sd),
  prior(lkj(2), class = cor)
)

modellocationvariance_nonoverlapping <- brm(
    formula_1,
    prior = priors_hurdle,
    family = hurdle_gamma(),
    data = filter(d_GPS_nonoverlap, isWeekend == "Weekday"),
    cores = 64,
    chains = 2,
    warmup = 500,
    iter = 2000,
    control = list(adapt_delta = 0.99, max_treedepth = 15),
    backend = 'cmdstan')

pp_check(modellocationvariance_nonoverlapping, ndraws = 100) +
  xlim(c(-2, 20))
```

## Figure for Home Time and Depression

```{r}
modelHomeTimePercent_nonoverlapping <- readRDS(here("analysis_code", "models", "modelHomeTimePercent_nonoverlapping.rds"))

newdata <- modelHomeTimePercent_nonoverlapping$data

pred_data <- add_predicted_draws(modelHomeTimePercent_nonoverlapping, newdata = newdata, allow_new_levels = T)

pred_data_subj <- pred_data %>%
  group_by(Leave, d_epdst_sum, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100)

weekday_data <- pred_data_subj %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

newdata_grid <- expand_grid(
  Role = c("Father", "Mother"),
  Leave = c("Maternity Leave", "Paternity Leave"),
  d_epdst_sum = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18), 
  SleepQuality = 3,
  ParticipantID = NA
)

predictions <- modelHomeTimePercent_nonoverlapping %>%
  epred_draws(newdata = newdata_grid, re_formula = NA) %>%
  ungroup()

predictions_summary <- predictions %>%
  group_by(Role, Leave, d_epdst_sum) %>%
  summarise(
    mean_home_time = mean(.epred),
    ci_lower_80 = quantile(.epred, 0.055),
    ci_upper_80 = quantile(.epred, 0.945),
    ci_lower_95 = quantile(.epred, 0.975),
    ci_upper_95 = quantile(.epred, 0.025),
    .groups = "drop"
  ) %>%
  arrange(Role, Leave, d_epdst_sum) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

HomeTimePlot_nonoverlapping <- ggplot() +
  geom_smooth(aes(x = d_epdst_sum, y = mean_home_time * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_smooth(aes(x = d_epdst_sum, y = ci_lower_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_smooth(aes(x = d_epdst_sum, y = ci_upper_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_point(alpha = 0.9, size = 3, position = position_jitter(width = 0.1), aes(x = as.numeric(d_epdst_sum) - 1, y = mean, color = Role, fill = Role), data = filter(weekday_data, OnLeave == "On Leave")) +
  facet_wrap(~Role, ncol = 2) +
  scale_y_continuous(breaks = seq(40, 100, 10), limit = c(39, 100)) +
  scale_x_continuous(breaks = seq(0, 20, 5)) +
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Edinburgh Postnatal Depression Score", y = "Predicted Home Time (%)") +
  ggtitle('A) Home Time by Postnatal Depression Score') +
  theme_minimal() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, color = "black", hjust = 0.5, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(3, "lines"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))
HomeTimePlot_nonoverlapping
```

## Posterior Predictions Plot, Depression

```{r}
modelmaxdistance_nonoverlapping <- readRDS(here("analysis_code", "models", "modelmaxdistance_nonoverlapping.rds"))
modellocationvariance_nonoverlapping <- readRDS(here("analysis_code", "models", "modellocationvariance_nonoverlapping.rds"))

# Model 2: Max Dist
maxdist1 <- as_draws_df(modelmaxdistance_nonoverlapping)

# Model 2: Home Time Percent
HPer1 <- as_draws_df(modelHomeTimePercent_nonoverlapping)

# Model 3: Location Variance
LocVar1 <- as_draws_df(modellocationvariance_nonoverlapping)

# MODEL 1: Max Distance - Distance and Hurdle effects
model1_mother_distance <- maxdist1$`bsp_RoleMother:mod_epdst_sum`
model1_father_distance <- maxdist1$`bsp_RoleFather:mod_epdst_sum` + maxdist1$`bsp_RoleFather:mod_epdst_sum:LeavePaternityLeave`
model1_mother_hurdle <- exp(maxdist1$`bsp_hu_RoleMother:mod_epdst_sum`)
model1_father_hurdle <- exp(maxdist1$`bsp_hu_RoleFather:mod_epdst_sum` + maxdist1$`bsp_hu_RoleFather:mod_epdst_sum:LeavePaternityLeave`)

# MODEL 2: Home Time Percent - Main effect and TOTAL (zoi + coi) effects
model2_mother_distance <- HPer1$`bsp_LeaveMaternityLeave:mod_epdst_sum` + HPer1$`bsp_LeaveMaternityLeave:mod_epdst_sum:RoleMother`
model2_father_distance <- HPer1$`bsp_LeavePaternityLeave:mod_epdst_sum`
model2_mother_hurdle <- exp(HPer1$`bsp_zoi_LeaveMaternityLeave:mod_epdst_sum` + HPer1$`bsp_zoi_LeaveMaternityLeave:mod_epdst_sum:RoleMother` + 
                           HPer1$`bsp_coi_LeaveMaternityLeave:mod_epdst_sum` + HPer1$`bsp_coi_LeaveMaternityLeave:mod_epdst_sum:RoleMother`)
model2_father_hurdle <- exp(HPer1$`bsp_zoi_LeavePaternityLeave:mod_epdst_sum` + HPer1$`bsp_coi_LeavePaternityLeave:mod_epdst_sum`)

# MODEL 3: Location Variance - Distance and Hurdle effects
model3_mother_distance <- LocVar1$`bsp_RoleMother:mod_epdst_sum`
model3_father_distance <- LocVar1$`bsp_RoleFather:mod_epdst_sum` + LocVar1$`bsp_RoleFather:mod_epdst_sum:LeavePaternityLeave`
model3_mother_hurdle <- exp(LocVar1$`bsp_hu_RoleMother:mod_epdst_sum`)
model3_father_hurdle <- exp(LocVar1$`bsp_hu_RoleFather:mod_epdst_sum` + LocVar1$`bsp_hu_RoleFather:mod_epdst_sum:LeavePaternityLeave`)

# Model 1 data
model1_data <- data.frame(
  model = "Max Distance",
  mother_distance = model1_mother_distance,
  father_distance = model1_father_distance,
  mother_hurdle = model1_mother_hurdle,
  father_hurdle = model1_father_hurdle
)

# Model 2 data
model2_data <- data.frame(
  model = "Home Time %",
  mother_distance = model2_mother_distance,
  father_distance = model2_father_distance,
  mother_hurdle = model2_mother_hurdle,
  father_hurdle = model2_father_hurdle
)

# Model 3 data
model3_data <- data.frame(
  model = "Location Variance",
  mother_distance = model3_mother_distance,
  father_distance = model3_father_distance,
  mother_hurdle = model3_mother_hurdle,
  father_hurdle = model3_father_hurdle
)

all_model_data <- rbind(model1_data, model2_data, model3_data)

distance_data <- all_model_data %>%
  select(model, mother_distance, father_distance) %>%
  pivot_longer(cols = c(mother_distance, father_distance),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_distance", "Mother", "Father"),
    parameter_type = "Distance Effect"
  )

hurdle_data <- all_model_data %>%
  select(model, mother_hurdle, father_hurdle) %>%
  pivot_longer(cols = c(mother_hurdle, father_hurdle),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_hurdle", "Mother", "Father"),
    parameter_type = "Hurdle Effect (OR)"
  )

# Calculate summary statistics for dot plots
distance_summary_detailed <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

hurdle_summary_detailed <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

# Distance effects summary
distance_summary <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median_effect = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_negative = mean(effect_size < 0, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)

# Hurdle effects summary
hurdle_summary <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median_or = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_increase_staying = mean(effect_size > 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)


MainEffectsPlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.028,
                      data = distance_data) +
  
  # 95% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = distance_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = distance_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = distance_summary_detailed) +
  
  # Median points - shifted down by 0.1
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = distance_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = distance_summary_detailed) +
  
  # Reference line
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  #scale_fill_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  #scale_color_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Change Per Depression Point", 
       y = "", 
       title = "B) Mobility Response to Depression Symptoms", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(-0.5, 0.35)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

HurdlePlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.05,
                      data = hurdle_data) +
  # 95% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = hurdle_summary_detailed) +
  
  # Median points - shifted down by 0.15
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = hurdle_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = hurdle_summary_detailed) +
  
  # Reference line (OR = 1)
  geom_vline(xintercept = 1, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Odds Ratio Per Depression Point", 
       y = "", 
       title = "C) Odds of Staying Home by Depression Level", 
       fill = "Role") +
  
  guides(color = "none") +
  xlim(c(0.5, 4)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.8),
    legend.key.size = unit(2, "lines"),
    legend.text = element_text(size = 18),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))

ChangeForDepression <- plot_grid(MainEffectsPlot, NULL, HurdlePlot, ncol = 3, rel_widths = c(0.5, 0.02, 0.5))

DepressionPlots <- plot_grid(HomeTimePlot_nonoverlapping, NULL, ChangeForDepression, nrow = 3, rel_heights = c(0.5, 0.1, 0.5))

#ggsave(plot = DepressionPlots, file = '/work/Paternity-leave/01. BarselProject/niels_geospatial/analysis_code/QuickPlots/FiguresForPaper/DepressionPlots_nonoverlapping.pdf', height = 14, width = 15)
```

## Extract Statistics for Depression

```{r}
# Calculate evidence ratios for all effects
# MODEL 1: Max Distance
model1_results <- list(
  mother_distance = calculate_evidence_ratio(model1_mother_distance, 0, "less"),
  father_distance = calculate_evidence_ratio(model1_father_distance, 0, "less"),
  mother_hurdle = calculate_evidence_ratio(model1_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model1_father_hurdle, 1, "greater")
)

# MODEL 2: Home Time Percent
model2_results <- list(
  mother_distance = calculate_evidence_ratio(model2_mother_distance, 0, "greater"),
  father_distance = calculate_evidence_ratio(model2_father_distance, 0, "greater"),
  mother_hurdle = calculate_evidence_ratio(model2_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model2_father_hurdle, 1, "greater")
)

# MODEL 3: Location Variance
model3_results <- list(
  mother_distance = calculate_evidence_ratio(model3_mother_distance, 0, "less"),
  father_distance = calculate_evidence_ratio(model3_father_distance, 0, "less"),
  mother_hurdle = calculate_evidence_ratio(model3_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model3_father_hurdle, 1, "greater")
)

# MOTHER VS FATHER COMPARISONS
# Calculate evidence ratios for differences between mothers and fathers
# MODEL 1: Max Distance - Mother vs Father comparisons
model1_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model1_mother_distance, model1_father_distance, 0, "less"), # mothers more negative?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model1_mother_hurdle), log(model1_father_hurdle), 0, "less") # mothers higher odds?
)

# MODEL 2: Home Time Percent - Mother vs Father comparisons  
model2_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model2_mother_distance, model2_father_distance, 0, "greater"), # mothers more positive?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model2_mother_hurdle), log(model2_father_hurdle), 0, "greater") # mothers higher odds?
)

# MODEL 3: Location Variance - Mother vs Father comparisons
model3_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model3_mother_distance, model3_father_distance, 0, "less"), # mothers more negative?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model3_mother_hurdle), log(model3_father_hurdle), 0, "greater") # mothers higher odds?
)

depression_hypothesis_results <- tibble(
  # MODEL 1: Max Distance - Individual Effects
  Test = c("Mother_MaxDist_Decrease", "Father_MaxDist_Decrease", 
           "Mother_MaxDist_StayHome", "Father_MaxDist_StayHome",
           # MODEL 2: Home Time - Individual Effects  
           "Mother_HomeTime_Increase", "Father_HomeTime_Increase",
           "Mother_HomeTime_CompleteStay", "Father_HomeTime_CompleteStay",
           # MODEL 3: Location Variance - Individual Effects
           "Mother_LocVar_Decrease", "Father_LocVar_Decrease",
           "Mother_LocVar_StayHome", "Father_LocVar_StayHome",
           # MODEL 1: Max Distance - Mother vs Father Comparisons
           "MotherVsFather_MaxDist_GreaterDecrease", "MotherVsFather_MaxDist_SmallerStayOdds",
           # MODEL 2: Home Time - Mother vs Father Comparisons
           "MotherVsFather_HomeTime_GreaterIncrease", "MotherVsFather_HomeTime_HigherStayOdds", 
           # MODEL 3: Location Variance - Mother vs Father Comparisons
           "MotherVsFather_LocVar_GreaterDecrease", "MotherVsFather_LocVar_HigherStayOdds"),
  
  # Extract median estimates (you'll need to calculate these from your posterior draws)
  Estimate = c(
    # Model 1 estimates - replace with actual medians
    median(model1_mother_distance), median(model1_father_distance),
    median(model1_mother_hurdle), median(model1_father_hurdle),
    # Model 2 estimates
    median(model2_mother_distance), median(model2_father_distance), 
    median(model2_mother_hurdle), median(model2_father_hurdle),
    # Model 3 estimates
    median(model3_mother_distance), median(model3_father_distance),
    median(model3_mother_hurdle), median(model3_father_hurdle),
    # Comparison estimates (differences)
    median(model1_mother_distance - model1_father_distance),
    median(log(model1_mother_hurdle) - log(model1_father_hurdle)),
    median(model2_mother_distance - model2_father_distance),
    median(log(model2_mother_hurdle) - log(model2_father_hurdle)),
    median(model3_mother_distance - model3_father_distance),
    median(log(model3_mother_hurdle) - log(model3_father_hurdle))
  ),
  
  # Calculate 95% credible intervals
  CI_Lower = c(
    # Model 1 CIs - replace with actual quantiles
    quantile(model1_mother_distance, 0.025), quantile(model1_father_distance, 0.025),
    quantile(model1_mother_hurdle, 0.025), quantile(model1_father_hurdle, 0.025),
    # Model 2 CIs
    quantile(model2_mother_distance, 0.025), quantile(model2_father_distance, 0.025),
    quantile(model2_mother_hurdle, 0.025), quantile(model2_father_hurdle, 0.025),
    # Model 3 CIs
    quantile(model3_mother_distance, 0.025), quantile(model3_father_distance, 0.025),
    quantile(model3_mother_hurdle, 0.025), quantile(model3_father_hurdle, 0.025),
    # Comparison CIs
    quantile(model1_mother_distance - model1_father_distance, 0.025),
    quantile(log(model1_mother_hurdle) - log(model1_father_hurdle), 0.025),
    quantile(model2_mother_distance - model2_father_distance, 0.025),
    quantile(log(model2_mother_hurdle) - log(model2_father_hurdle), 0.025),
    quantile(model3_mother_distance - model3_father_distance, 0.025),
    quantile(log(model3_mother_hurdle) - log(model3_father_hurdle), 0.025)
  ),
  
  CI_Upper = c(
    # Model 1 CIs - replace with actual quantiles
    quantile(model1_mother_distance, 0.975), quantile(model1_father_distance, 0.975),
    quantile(model1_mother_hurdle, 0.975), quantile(model1_father_hurdle, 0.975),
    # Model 2 CIs
    quantile(model2_mother_distance, 0.975), quantile(model2_father_distance, 0.975),
    quantile(model2_mother_hurdle, 0.975), quantile(model2_father_hurdle, 0.975),
    # Model 3 CIs
    quantile(model3_mother_distance, 0.975), quantile(model3_father_distance, 0.975),
    quantile(model3_mother_hurdle, 0.975), quantile(model3_father_hurdle, 0.975),
    # Comparison CIs
    quantile(model1_mother_distance - model1_father_distance, 0.975),
    quantile(log(model1_mother_hurdle) - log(model1_father_hurdle), 0.975),
    quantile(model2_mother_distance - model2_father_distance, 0.975),
    quantile(log(model2_mother_hurdle) - log(model2_father_hurdle), 0.975),
    quantile(model3_mother_distance - model3_father_distance, 0.975),
    quantile(log(model3_mother_hurdle) - log(model3_father_hurdle), 0.975)
  ),
  
  # Extract evidence ratios from your calculated results
  EvidenceRatio = c(
    model1_results$mother_distance$evidence_ratio, model1_results$father_distance$evidence_ratio,
    model1_results$mother_hurdle$evidence_ratio, model1_results$father_hurdle$evidence_ratio,
    model2_results$mother_distance$evidence_ratio, model2_results$father_distance$evidence_ratio,
    model2_results$mother_hurdle$evidence_ratio, model2_results$father_hurdle$evidence_ratio,
    model3_results$mother_distance$evidence_ratio, model3_results$father_distance$evidence_ratio,
    model3_results$mother_hurdle$evidence_ratio, model3_results$father_hurdle$evidence_ratio,
    model1_comparisons$distance_diff$evidence_ratio, model1_comparisons$hurdle_ratio$evidence_ratio,
    model2_comparisons$distance_diff$evidence_ratio, model2_comparisons$hurdle_ratio$evidence_ratio,
    model3_comparisons$distance_diff$evidence_ratio, model3_comparisons$hurdle_ratio$evidence_ratio
  ),
  
  # Extract posterior probabilities
  PostProb = c(
    model1_results$mother_distance$probability, model1_results$father_distance$probability,
    model1_results$mother_hurdle$probability, model1_results$father_hurdle$probability,
    model2_results$mother_distance$probability, model2_results$father_distance$probability,
    model2_results$mother_hurdle$probability, model2_results$father_hurdle$probability,
    model3_results$mother_distance$probability, model3_results$father_distance$probability,
    model3_results$mother_hurdle$probability, model3_results$father_hurdle$probability,
    model1_comparisons$distance_diff$probability, model1_comparisons$hurdle_ratio$probability,
    model2_comparisons$distance_diff$probability, model2_comparisons$hurdle_ratio$probability,
    model3_comparisons$distance_diff$probability, model3_comparisons$hurdle_ratio$probability
  )
) %>%
  mutate(
    # Round all numeric values
    Estimate = round(Estimate, 2),
    CI_Lower = round(CI_Lower, 2), 
    CI_Upper = round(CI_Upper, 2),
    EvidenceRatio = round(EvidenceRatio, 1),
    PostProb = round(PostProb, 2),
    # Create odds ratios for hurdle effects
    OddsRatio = ifelse(grepl("StayHome|Stay", Test), round(exp(Estimate), 2), NA),
    OR_CI_Lower = ifelse(grepl("StayHome|Stay", Test), round(exp(CI_Lower), 2), NA),
    OR_CI_Upper = ifelse(grepl("StayHome|Stay", Test), round(exp(CI_Upper), 2), NA)
  )

# Create the main stats table (similar to your SDEStats format)
depression_stats <- depression_hypothesis_results %>%
  select(TestDescription = Test, Estimate, CI_Lower, CI_Upper, Evid.Ratio = EvidenceRatio, Post.Prob = PostProb) %>%
  mutate(
    # Format evidence ratio as string for easy LaTeX use
    Evid.Ratio = sprintf("%.1f", Evid.Ratio)
  )

# Create the summary stats table for wide format reference (similar to your system)
depression_summary_stats <- depression_hypothesis_results %>%
  pivot_longer(cols = c(Estimate, CI_Lower, CI_Upper, EvidenceRatio, PostProb, OddsRatio, OR_CI_Lower, OR_CI_Upper), 
               names_to = "Metric", values_to = "Value") %>%
  unite("Statistic", Test, Metric, sep = "_") %>%
  select(Statistic, Value) %>%
  filter(!is.na(Value)) %>%
  mutate(Value = round(Value, 3))


# Save to CSV files for Overleaf integration
write.csv(depression_summary_stats, here("analysis_code", "StatsForBodyText", "depressionspatial_summary_nonoverlapping.csv"), row.names = FALSE)
```

## Home Time and Sleep Quality

```{r}
newdata <- d_GPS_nonoverlap %>%
  group_by(ParticipantID, Role, Leave, SleepQuality) %>%
  summarise(n = n()) %>%
  mutate(d_epdst_sum = median(as.numeric(d_GPS_nonoverlap$d_epdst_sum))) %>%
  filter(SleepQuality %in% c('1', '2', '3', '4', '5')) %>%
  mutate(SleepQuality = factor(SleepQuality, levels = c('1', '2', '3', '4', '5'))) %>%
  mutate(SleepQuality = as.ordered(SleepQuality)) %>%
  print(n = 50)

pred_data <- add_predicted_draws(modelHomeTimePercent_nonoverlapping, newdata = newdata, allow_new_levels = T)

pred_data_subj <- pred_data %>%
  group_by(Leave, d_epdst_sum, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100)

pred_data_subj <- pred_data %>%
  group_by(Leave, SleepQuality, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100) %>%
  mutate(SleepQuality_factor = factor(SleepQuality, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))

weekday_data <- pred_data_subj %>% #filter(isWeekend == "Weekday") %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

newdata_grid <- expand_grid(
  Role = c("Father", "Mother"),
  Leave = c("Maternity Leave", "Paternity Leave"),
  d_epdst_sum = c(5), 
  SleepQuality = c(1, 2, 3, 4, 5),
  ParticipantID = NA
)

predictions <- modelHomeTimePercent_nonoverlapping %>%
  epred_draws(newdata = newdata_grid, re_formula = NA) %>%
  ungroup()

predictions_summary <- predictions %>%
  group_by(Role, Leave, SleepQuality) %>%
  summarise(
    mean_home_time = mean(.epred),
    ci_lower_80 = quantile(.epred, 0.055),
    ci_upper_80 = quantile(.epred, 0.945),
    ci_lower_95 = quantile(.epred, 0.975),
    ci_upper_95 = quantile(.epred, 0.025),
    .groups = "drop"
  ) %>%
  arrange(Role, Leave, SleepQuality) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ),
  SleepQuality_factor = factor(SleepQuality, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))
  
HomeTimeSleepPlot <- ggplot() +
  geom_smooth(aes(x = SleepQuality, y = mean_home_time * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_smooth(aes(x = SleepQuality, y = ci_lower_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_smooth(aes(x = SleepQuality, y = ci_upper_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "On Leave")) +
  geom_point(alpha = 0.9, size = 3, position = position_jitter(width = 0.1), aes(x = as.numeric(SleepQuality), y = mean, color = Role, fill = Role), data = filter(weekday_data, OnLeave == "On Leave")) +
  facet_wrap(~Role, ncol = 2) +
  scale_y_continuous(breaks = seq(20, 100, 10), limit = c(20, 100)) +
  scale_x_continuous(breaks = seq(1, 5, 1), limit = c(0, 5), labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")) +
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Reported Sleep Quality", y = "Predicted Home Time (%)") +
  ggtitle('A) Home Time by Daily Sleep Quality') +
  theme_minimal() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, color = "black", hjust = 0.5, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(3, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))
```

## Posterior Predictions Plot, Sleep

```{r}
maxdist2 <- as_draws_df(modelmaxdistance_nonoverlapping)
HPer2 <- as_draws_df(modelHomeTimePercent_nonoverlapping)
LocVar2 <- as_draws_df(modellocationvariance_nonoverlapping)

# MODEL 1: Max Distance - Distance and Hurdle effects
model1_mother_distance <- maxdist2$`bsp_RoleMother:moSleepQuality`
model1_father_distance <- maxdist2$`bsp_RoleFather:moSleepQuality` + maxdist2$`bsp_RoleFather:moSleepQuality:LeavePaternityLeave`
model1_mother_hurdle <- exp(maxdist2$`bsp_hu_RoleMother:moSleepQuality`)
model1_father_hurdle <- exp(maxdist2$`bsp_hu_RoleFather:moSleepQuality` + maxdist2$`bsp_hu_RoleFather:moSleepQuality:LeavePaternityLeave`)

# MODEL 2: Home Time Percent - Main effect and COI (complete inflation) effects
model2_mother_distance <- HPer2$`bsp_LeaveMaternityLeave:moSleepQuality:RoleMother`
model2_father_distance <- HPer2$`bsp_LeavePaternityLeave:moSleepQuality`
model2_mother_hurdle <- exp(HPer2$`bsp_coi_LeaveMaternityLeave:moSleepQuality` + HPer2$`bsp_coi_LeaveMaternityLeave:moSleepQuality:RoleMother`)
model2_father_hurdle <- exp(HPer2$`bsp_coi_LeavePaternityLeave:moSleepQuality`)

# MODEL 2: Home Time Percent - Main effect and TOTAL (zoi + coi) effects
model2_mother_distance <- HPer2$`bsp_LeaveMaternityLeave:moSleepQuality` + HPer2$`bsp_LeaveMaternityLeave:moSleepQuality:RoleMother`
model2_father_distance <- HPer2$`bsp_LeavePaternityLeave:moSleepQuality`
model2_mother_hurdle <- exp(HPer2$`bsp_zoi_LeaveMaternityLeave:moSleepQuality` + HPer2$`bsp_zoi_LeaveMaternityLeave:moSleepQuality:RoleMother` + 
                           HPer2$`bsp_coi_LeaveMaternityLeave:moSleepQuality` + HPer2$`bsp_coi_LeaveMaternityLeave:moSleepQuality:RoleMother`)
model2_father_hurdle <- exp(HPer2$`bsp_zoi_LeavePaternityLeave:moSleepQuality` + HPer2$`bsp_coi_LeavePaternityLeave:moSleepQuality`)

# MODEL 3: Location Variance - Distance and Hurdle effects
model3_mother_distance <- LocVar2$`bsp_RoleMother:moSleepQuality`
model3_father_distance <- LocVar2$`bsp_RoleFather:moSleepQuality` + LocVar2$`bsp_RoleFather:moSleepQuality:LeavePaternityLeave`
model3_mother_hurdle <- exp(LocVar2$`bsp_hu_RoleMother:moSleepQuality`)
model3_father_hurdle <- exp(LocVar2$`bsp_hu_RoleFather:moSleepQuality` + LocVar2$`bsp_hu_RoleFather:moSleepQuality:LeavePaternityLeave`)

# Model 1 data
model1_data <- data.frame(
  model = "Max Distance",
  mother_distance = model1_mother_distance,
  father_distance = model1_father_distance,
  mother_hurdle = model1_mother_hurdle,
  father_hurdle = model1_father_hurdle
)

# Model 2 data
model2_data <- data.frame(
  model = "Home Time %",
  mother_distance = model2_mother_distance,
  father_distance = model2_father_distance,
  mother_hurdle = model2_mother_hurdle,
  father_hurdle = model2_father_hurdle
)

# Model 3 data
model3_data <- data.frame(
  model = "Location Variance",
  mother_distance = model3_mother_distance,
  father_distance = model3_father_distance,
  mother_hurdle = model3_mother_hurdle,
  father_hurdle = model3_father_hurdle
)

all_model_data <- rbind(model1_data, model2_data, model3_data)

distance_data <- all_model_data %>%
  select(model, mother_distance, father_distance) %>%
  pivot_longer(cols = c(mother_distance, father_distance),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_distance", "Mother", "Father"),
    parameter_type = "Distance Effect"
  )

hurdle_data <- all_model_data %>%
  select(model, mother_hurdle, father_hurdle) %>%
  pivot_longer(cols = c(mother_hurdle, father_hurdle),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_hurdle", "Mother", "Father"),
    parameter_type = "Hurdle Effect (OR)"
  )

# Calculate summary statistics for dot plots
distance_summary_detailed <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

hurdle_summary_detailed <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

# Distance effects summary
distance_summary <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median_effect = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_negative = mean(effect_size < 0, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)

# Hurdle effects summary
hurdle_summary <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median_or = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_increase_staying = mean(effect_size > 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)


MainEffectsPlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.05,
                      data = distance_data) +
  
  # 95% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = distance_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = distance_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = distance_summary_detailed) +
  
  # Median points - shifted down by 0.1
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = distance_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = distance_summary_detailed) +
  
  # Reference line
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  #scale_fill_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  #scale_color_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Change Per Sleep Category", 
       y = "", 
       title = "B) Mobility Response to Sleep Quality", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  #xlim(c(-0.5, 0.35)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

HurdlePlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.07,
                      data = hurdle_data) +
  # 95% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = hurdle_summary_detailed) +
  
  # Median points - shifted down by 0.15
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = hurdle_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = hurdle_summary_detailed) +
  
  # Reference line (OR = 1)
  geom_vline(xintercept = 1, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Odds Ratio Per Sleep Point", 
       y = "", 
       title = "C) Odds of Staying Home by Sleep Quality", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(0.2, 3)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.8),
    legend.key.size = unit(2, "lines"),
    legend.text = element_text(size = 18),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))

ChangeForSleep <- plot_grid(MainEffectsPlot, NULL, HurdlePlot, ncol = 3, rel_widths = c(0.5, 0.02, 0.5))
ChangeForSleep

SleepPlots <- plot_grid(HomeTimeSleepPlot, NULL, ChangeForSleep, nrow = 3, rel_heights = c(0.5, 0.1, 0.5))

#ggsave(plot = SleepPlots, file = '/work/Paternity-leave/01. BarselProject/niels_geospatial/analysis_code/QuickPlots/FiguresForPaper/SleepPlots_nonoverlapping.pdf', height = 14, width = 15)
```

## Extract Statistics for Sleep

```{r}
# Calculate Evidence Ratios for Depression Effects on Mobility

# MODEL 1: Max Distance
model1_results <- list(
  mother_distance = calculate_evidence_ratio(model1_mother_distance, 0, "greater"),
  father_distance = calculate_evidence_ratio(model1_father_distance, 0, "less"),
  mother_hurdle = calculate_evidence_ratio(model1_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model1_father_hurdle, 1, "less")
)

# MODEL 2: Home Time Percent
model2_results <- list(
  mother_distance = calculate_evidence_ratio(model2_mother_distance, 0, "greater"),
  father_distance = calculate_evidence_ratio(model2_father_distance, 0, "greater"),
  mother_hurdle = calculate_evidence_ratio(model2_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model2_father_hurdle, 1, "greater")
)

# MODEL 3: Location Variance
model3_results <- list(
  mother_distance = calculate_evidence_ratio(model3_mother_distance, 0, "less"),
  father_distance = calculate_evidence_ratio(model3_father_distance, 0, "less"),
  mother_hurdle = calculate_evidence_ratio(model3_mother_hurdle, 1, "greater"),
  father_hurdle = calculate_evidence_ratio(model3_father_hurdle, 1, "greater")
)

# MOTHER VS FATHER COMPARISONS
# MODEL 1: Max Distance - Mother vs Father comparisons
model1_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model1_mother_distance, model1_father_distance, 0, "less"), # mothers more negative?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model1_mother_hurdle), log(model1_father_hurdle), 0, "less") # mothers higher odds?
)

# MODEL 2: Home Time Percent - Mother vs Father comparisons  
model2_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model2_mother_distance, model2_father_distance, 0, "greater"), # mothers more positive?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model2_mother_hurdle), log(model2_father_hurdle), 0, "greater") # mothers higher odds?
)

# MODEL 3: Location Variance - Mother vs Father comparisons
model3_comparisons <- list(
  distance_diff = calculate_difference_evidence_ratio(model3_mother_distance, model3_father_distance, 0, "less"), # mothers more negative?
  hurdle_ratio = calculate_difference_evidence_ratio(log(model3_mother_hurdle), log(model3_father_hurdle), 0, "greater") # mothers higher odds?
)

# Create comprehensive results tibble with all depression effects
depression_hypothesis_results <- tibble(
  # MODEL 1: Max Distance - Individual Effects
  Test = c("Mother_MaxDist_Decrease", "Father_MaxDist_Decrease", 
           "Mother_MaxDist_StayHome", "Father_MaxDist_StayHome",
           # MODEL 2: Home Time - Individual Effects  
           "Mother_HomeTime_Increase", "Father_HomeTime_Increase",
           "Mother_HomeTime_CompleteStay", "Father_HomeTime_CompleteStay",
           # MODEL 3: Location Variance - Individual Effects
           "Mother_LocVar_Decrease", "Father_LocVar_Decrease",
           "Mother_LocVar_StayHome", "Father_LocVar_StayHome",
           # MODEL 1: Max Distance - Mother vs Father Comparisons
           "MotherVsFather_MaxDist_GreaterDecrease", "MotherVsFather_MaxDist_SmallerStayOdds",
           # MODEL 2: Home Time - Mother vs Father Comparisons
           "MotherVsFather_HomeTime_GreaterIncrease", "MotherVsFather_HomeTime_HigherStayOdds", 
           # MODEL 3: Location Variance - Mother vs Father Comparisons
           "MotherVsFather_LocVar_GreaterDecrease", "MotherVsFather_LocVar_HigherStayOdds"),
  
  # Extract median estimates (you'll need to calculate these from your posterior draws)
  Estimate = c(
    # Model 1 estimates - replace with actual medians
    median(model1_mother_distance), median(model1_father_distance),
    median(model1_mother_hurdle), median(model1_father_hurdle),
    # Model 2 estimates
    median(model2_mother_distance), median(model2_father_distance), 
    median(model2_mother_hurdle), median(model2_father_hurdle),
    # Model 3 estimates
    median(model3_mother_distance), median(model3_father_distance),
    median(model3_mother_hurdle), median(model3_father_hurdle),
    # Comparison estimates (differences)
    median(model1_mother_distance - model1_father_distance),
    median(log(model1_mother_hurdle) - log(model1_father_hurdle)),
    median(model2_mother_distance - model2_father_distance),
    median(log(model2_mother_hurdle) - log(model2_father_hurdle)),
    median(model3_mother_distance - model3_father_distance),
    median(log(model3_mother_hurdle) - log(model3_father_hurdle))
  ),
  
  # Calculate 95% credible intervals
  CI_Lower = c(
    # Model 1 CIs - replace with actual quantiles
    quantile(model1_mother_distance, 0.025), quantile(model1_father_distance, 0.025),
    quantile(model1_mother_hurdle, 0.025), quantile(model1_father_hurdle, 0.025),
    # Model 2 CIs
    quantile(model2_mother_distance, 0.025), quantile(model2_father_distance, 0.025),
    quantile(model2_mother_hurdle, 0.025), quantile(model2_father_hurdle, 0.025),
    # Model 3 CIs
    quantile(model3_mother_distance, 0.025), quantile(model3_father_distance, 0.025),
    quantile(model3_mother_hurdle, 0.025), quantile(model3_father_hurdle, 0.025),
    # Comparison CIs
    quantile(model1_mother_distance - model1_father_distance, 0.025),
    quantile(log(model1_mother_hurdle) - log(model1_father_hurdle), 0.025),
    quantile(model2_mother_distance - model2_father_distance, 0.025),
    quantile(log(model2_mother_hurdle) - log(model2_father_hurdle), 0.025),
    quantile(model3_mother_distance - model3_father_distance, 0.025),
    quantile(log(model3_mother_hurdle) - log(model3_father_hurdle), 0.025)
  ),
  
  CI_Upper = c(
    # Model 1 CIs - replace with actual quantiles
    quantile(model1_mother_distance, 0.975), quantile(model1_father_distance, 0.975),
    quantile(model1_mother_hurdle, 0.975), quantile(model1_father_hurdle, 0.975),
    # Model 2 CIs
    quantile(model2_mother_distance, 0.975), quantile(model2_father_distance, 0.975),
    quantile(model2_mother_hurdle, 0.975), quantile(model2_father_hurdle, 0.975),
    # Model 3 CIs
    quantile(model3_mother_distance, 0.975), quantile(model3_father_distance, 0.975),
    quantile(model3_mother_hurdle, 0.975), quantile(model3_father_hurdle, 0.975),
    # Comparison CIs
    quantile(model1_mother_distance - model1_father_distance, 0.975),
    quantile(log(model1_mother_hurdle) - log(model1_father_hurdle), 0.975),
    quantile(model2_mother_distance - model2_father_distance, 0.975),
    quantile(log(model2_mother_hurdle) - log(model2_father_hurdle), 0.975),
    quantile(model3_mother_distance - model3_father_distance, 0.975),
    quantile(log(model3_mother_hurdle) - log(model3_father_hurdle), 0.975)
  ),
  
  # Extract evidence ratios from your calculated results
  EvidenceRatio = c(
    model1_results$mother_distance$evidence_ratio, model1_results$father_distance$evidence_ratio,
    model1_results$mother_hurdle$evidence_ratio, model1_results$father_hurdle$evidence_ratio,
    model2_results$mother_distance$evidence_ratio, model2_results$father_distance$evidence_ratio,
    model2_results$mother_hurdle$evidence_ratio, model2_results$father_hurdle$evidence_ratio,
    model3_results$mother_distance$evidence_ratio, model3_results$father_distance$evidence_ratio,
    model3_results$mother_hurdle$evidence_ratio, model3_results$father_hurdle$evidence_ratio,
    model1_comparisons$distance_diff$evidence_ratio, model1_comparisons$hurdle_ratio$evidence_ratio,
    model2_comparisons$distance_diff$evidence_ratio, model2_comparisons$hurdle_ratio$evidence_ratio,
    model3_comparisons$distance_diff$evidence_ratio, model3_comparisons$hurdle_ratio$evidence_ratio
  ),
  
  # Extract posterior probabilities
  PostProb = c(
    model1_results$mother_distance$probability, model1_results$father_distance$probability,
    model1_results$mother_hurdle$probability, model1_results$father_hurdle$probability,
    model2_results$mother_distance$probability, model2_results$father_distance$probability,
    model2_results$mother_hurdle$probability, model2_results$father_hurdle$probability,
    model3_results$mother_distance$probability, model3_results$father_distance$probability,
    model3_results$mother_hurdle$probability, model3_results$father_hurdle$probability,
    model1_comparisons$distance_diff$probability, model1_comparisons$hurdle_ratio$probability,
    model2_comparisons$distance_diff$probability, model2_comparisons$hurdle_ratio$probability,
    model3_comparisons$distance_diff$probability, model3_comparisons$hurdle_ratio$probability
  )
) %>%
  mutate(
    # Round all numeric values
    Estimate = round(Estimate, 2),
    CI_Lower = round(CI_Lower, 2), 
    CI_Upper = round(CI_Upper, 2),
    EvidenceRatio = round(EvidenceRatio, 1),
    PostProb = round(PostProb, 2),
    # Create odds ratios for hurdle effects
    OddsRatio = ifelse(grepl("StayHome|Stay", Test), round(exp(Estimate), 2), NA),
    OR_CI_Lower = ifelse(grepl("StayHome|Stay", Test), round(exp(CI_Lower), 2), NA),
    OR_CI_Upper = ifelse(grepl("StayHome|Stay", Test), round(exp(CI_Upper), 2), NA)
  )

# Create the main stats table (similar to your SDEStats format)
depression_stats <- depression_hypothesis_results %>%
  select(TestDescription = Test, Estimate, CI_Lower, CI_Upper, Evid.Ratio = EvidenceRatio, Post.Prob = PostProb) %>%
  mutate(
    # Format evidence ratio as string for easy LaTeX use
    Evid.Ratio = sprintf("%.1f", Evid.Ratio)
  )

# Create the summary stats table for wide format reference (similar to your system)
depression_summary_stats <- depression_hypothesis_results %>%
  pivot_longer(cols = c(Estimate, CI_Lower, CI_Upper, EvidenceRatio, PostProb, OddsRatio, OR_CI_Lower, OR_CI_Upper), 
               names_to = "Metric", values_to = "Value") %>%
  unite("Statistic", Test, Metric, sep = "_") %>%
  select(Statistic, Value) %>%
  filter(!is.na(Value)) %>%
  mutate(Value = round(Value, 3))


# Save to CSV files for Overleaf integration
write.csv(depression_summary_stats, here("analysis_code", "StatsForBodyText", "sleepspatial_summary_nonoverlapping.csv"), row.names = FALSE)
```

# Run Models on Weekend Data
## Figures
### Mobility Range Plot

```{r}
DistancePredictionsData <- rbind(extract_model_predictions_weekend(model_maxDistanceFromHomeKm_simple, "Max Distance"), 
                                 extract_model_predictions_weekend(model_radiusOfGyrationKm_simple, "Radius Of Gyration"))

DistancePredictionsData <- get_subject_predictions_med(model_maxDistanceFromHomeKm_simple) %>% mutate(Metric = "Max Distance")
RadiusPredictionsData <- get_subject_predictions_med(model_radiusOfGyrationKm_simple) %>% mutate(Metric = "Radius of Gyration")
  
DistancePredictionsData <- rbind(DistancePredictionsData, RadiusPredictionsData) %>%
  filter(isWeekend == "Weekend") %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

combined_dot_interval_plot <- ggplot(DistancePredictionsData, aes(y = 0, x = median_pred, color = OnLeave, fill = OnLeave)) +
  stat_dots(quantiles = 150, .width = c(0.5, 0.89), point_interval = "median_qi", dotsize = 1, alpha = 0.9, side = "both") +
  stat_pointinterval(aes(x = median_pred, y = - 0.7), data = DistancePredictionsData, .width = c(.66, .95), position = position_dodge(width = 0.4)) +
  xlim(c(0, 10)) +
  facet_grid2(Role ~ Metric, scales = "free", independent = "y", switch = "y") +
  scale_color_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  labs(title = "A) Mobility Range", 
       x = "Kilometers",
       y = "", 
       color = "Leave Status",
       fill = "Leave Status") +
  expand_limits(x = 0) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 15, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(2, "cm"),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))
```

### Home Time Percentage

```{r}
HPer_preds <- get_subject_predictions_HPer(modelHomeTimePercent_simple) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

HPer_preds_clean <- HPer_preds %>%
  filter(isWeekend == "Weekend") %>%
  mutate(
    Condition = case_when(
      OnLeave == "Not On Leave" ~ "Not On Leave",
      OnLeave == "On Leave" ~ "On Leave"
    ),
    Condition = factor(Condition, levels = c("On Leave", "Not On Leave")),
    median_pred = median_pred * 100
  )
set.seed(123) 

HPer_jittered <- HPer_preds_clean %>%
  mutate(
    Condition_num = as.numeric(Condition),
    Condition_dodged = case_when(
      Condition == "On Leave" ~ Condition_num - 0.25,
      Condition == "Not On Leave" ~ Condition_num + 0.25
    ),
    Condition_jittered = Condition_num + runif(n(), -0.1, 0.05)
  )


HPer_Plot <- ggplot(HPer_jittered, aes(fill = Condition, color = Condition)) +
  geom_path(aes(x = Condition_jittered, y = median_pred, group = ParticipantID), 
            alpha = 0.3, color = "gray60", linewidth = 0.5) +
  geom_boxplot(aes(x = Condition_dodged, y = median_pred), 
               width = 0.1, alpha = 0.9, outlier.shape = NA, 
               color = "black") +
  geom_point(aes(x = Condition_jittered, y = median_pred), 
             alpha = 0.8, size = 1.5) +
  facet_wrap(~Role) +
  scale_color_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  scale_x_continuous(breaks = c(1, 2), labels = c("On Leave", "Not On Leave")) +
  labs(x = '', y = 'Home Time (%)') +
  guides(color = guide_legend(reverse = TRUE), fill = guide_legend(reverse = TRUE)) +
  ylim(c(42, 85)) +
  ggtitle('B) Home Time During Daytime Hours') +
  theme_bw() + 
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_blank(),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))

HPer_Plot
```

### Ellipsis Plot

```{r}
get_subject_predictions <- function(model) {
  
  # Use the model's original data
  newdata <- model$data
  
  # Get predictions with random effects
  pred_data <- add_predicted_draws(model, newdata = newdata, allow_new_levels = TRUE)
  
  # Get median prediction for each observation
  pred_summary <- pred_data %>%
    group_by(Role, Leave, ParticipantID, isWeekend) %>%
    summarise(median_pred = median(.prediction), .groups = "drop")
  
  return(pred_summary)
}

SDE_preds <- get_subject_predictions(model_SDE_simple) %>% #filter(isWeekend == "Weekday") %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  )) 

# Calculate summary statistics for ellipse areas
SDE_summary <- SDE_preds %>%
  filter(isWeekend == "Weekend") %>%  # Focus on weekdays
  group_by(Role, OnLeave) %>%
  summarise(
    median_area = median(median_pred),
    mean_area = mean(median_pred),
    q25 = quantile(median_pred, 0.25),
    q75 = quantile(median_pred, 0.75),
    sd_area = sd(median_pred),
    .groups = "drop"
  ) %>%
  mutate(
    # Convert areas to radii for plotting (assuming circular approximation)
    radius_median = sqrt(median_area / pi),
    radius_q25 = sqrt(q25 / pi),
    radius_q75 = sqrt(q75 / pi),
    
    # Position ellipses on same row
    x_pos = case_when(
      Role == "Father" & OnLeave == "Not On Leave" ~ 2,
      Role == "Father" & OnLeave == "On Leave" ~ 1,
      Role == "Mother" & OnLeave == "Not On Leave" ~ 4,
      Role == "Mother" & OnLeave == "On Leave" ~ 3
    ),
    y_pos = 0.85,  # All on same row
    
    # Create labels
    condition_label = paste(Role, "-", OnLeave)
  )

# Merge with SDE summary
SDE_summary_enhanced <- SDE_summary
  #left_join(maj2min_summary, by = c("Role", "OnLeave")) %>%
  #left_join(gravcompact_summary, by = c("Role", "OnLeave"))


SDE_summary <- extract_model_predictions_weekend(model_SDE_simple, "SDE") %>%
  group_by(Role, OnLeave) %>%
  summarise(
    median_area = median(value),
    mean_area = mean(value),
    q25 = quantile(value, 0.25),
    q75 = quantile(value, 0.75),
    sd_area = sd(value),
    .groups = "drop"
  ) %>%
  mutate(
    # Convert areas to radii for plotting (assuming circular approximation)
    radius_median = sqrt(median_area / pi),
    radius_q25 = sqrt(q25 / pi),
    radius_q75 = sqrt(q75 / pi),
    # Position ellipses on same row
    x_pos = case_when(
      Role == "Father" & OnLeave == "Not On Leave" ~ 2,
      Role == "Father" & OnLeave == "On Leave" ~ 1,
      Role == "Mother" & OnLeave == "Not On Leave" ~ 4,
      Role == "Mother" & OnLeave == "On Leave" ~ 3
    ),
    y_pos = 0.85,  # All on same row
    condition_label = paste(Role, "-", OnLeave)
  )

# Modified radar plot to show only SDE (area) as triangles
create_sde_area_radar <- function() {
  
  # Prepare data for SDE area visualization only
  sde_area_data <- SDE_summary_enhanced %>%
    filter(Role %in% c("Father", "Mother")) %>%
    mutate(condition = paste(Role, OnLeave, sep = " - ")) %>%
    select(condition, Role, OnLeave, median_area)
  
  # Create triangle coordinates for each condition
  # Each triangle represents the mean ellipse area as a regular triangle
  triangle_coords <- sde_area_data %>%
    expand_grid(vertex = 1:3) %>%
    mutate(
      # Calculate angles for triangle vertices (starting from top)
      angle = (vertex - 1) * 2*pi/3 - pi/2,  # -pi/2 to start from top
      
      # Scale the triangle size based on actual area (no normalization)
      radius = sqrt(median_area / pi),  # Convert area to radius for visualization
      
      # Calculate x,y coordinates
      x = radius * cos(angle),
      y = radius * sin(angle)
    ) %>%
    # Close the triangle by adding the first vertex at the end
    group_by(condition, Role, OnLeave) %>%
    arrange(vertex) #%>%
    #bind_rows(slice(1)) %>%
    #ungroup()
  
  # Create background grid (circular) - adjust based on actual data range
  max_radius <- max(sqrt(sde_area_data$median_area / pi))
  grid_radii <- seq(0, max_radius, length.out = 5)[-1]  # Remove 0
  
  # Create grid data for each role to enable faceting
  grid_data <- expand_grid(
    Role = c("Father", "Mother"),
    radius = grid_radii,
    angle = seq(0, 2*pi, length.out = 100)
  ) %>%
    mutate(
      x = radius * cos(angle),
      y = radius * sin(angle)
    )
  
  # Create reference lines with actual area values for each role
  reference_lines <- expand_grid(
    Role = c("Father", "Mother"),
    radius = grid_radii
  ) %>%
    mutate(
      area = radius^2 * pi,  # Convert back to area for labels
      label = paste0(round(area, 1), " km")
    )
  
  # Create the plot
  radar_plot <- ggplot() +
    
    # Add background grid with stronger lines
    geom_path(data = grid_data, aes(x = x, y = y, group = interaction(Role, radius)), color = "black", alpha = 0.5, linetype = "dashed", size = 0.5) +
    
    # Add radial lines for better coordinate reference
    geom_segment(data = expand_grid(Role = c("Father", "Mother"), angle = seq(0, 2*pi, length.out = 9)[-9]), aes(x = 0, y = 0, xend = 1 * max_radius * cos(angle), yend = 1*max_radius * sin(angle)), color = "gray50", linetype = "dashed", alpha = 0.9, size = 0.3) +
    
    geom_text(data = reference_lines, aes(x = 0, y = radius + max_radius * 0.03, label = label), size = 3.5, color = "black", hjust = 0.5, vjust = 0, fontface = "bold") +
    
    # Add scale line markers
    geom_segment(data = reference_lines, aes(x = 0, y = radius - max_radius * 0.02, yend = radius + max_radius * 0.02, xend = 0), color = "gray50", size = 0.8) +
    
    # Add triangle areas (filled)
    geom_polygon(data = triangle_coords, aes(x = x, y = y, fill = OnLeave, group = condition), alpha = 0.4) +
    
    # Add triangle outlines (closed polygons)
    geom_polygon(data = triangle_coords, aes(x = x, y = y, color = OnLeave, group = condition), fill = NA, size = 1.5) +
    
    # Add points at triangle vertices
    #geom_point(data = filter(triangle_coords, vertex <= 3), aes(x = x, y = y, color = OnLeave), size = 3, stroke = 1, show.legend = F) +
    
    # Add center point for reference for each role
    geom_point(data = data.frame(Role = c("Father", "Mother"), x = 0, y = 0), aes(x = x, y = y), color = "black", size = 2, alpha = 1.5) +
    
    # Facet by role
    facet_wrap(~ Role) +
    
    # Scales
    scale_color_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
    scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
    
    # Coordinate system - adjust limits based on actual data
    coord_fixed(ratio = 1) +
    xlim(-max_radius * 1.3, max_radius * 1.3) + 
    ylim(-max_radius * 1.40, max_radius * 1.3) +
    
    # Theme
    theme_minimal() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      legend.title = element_blank(),
        legend.position = "top",
        legend.key.size = unit(1, "lines"),
        legend.text = element_text(size = 15),
        legend.background = element_rect(fill = "transparent", color = NA),
        legend.key = element_rect(fill = "transparent", color = NA),
        strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
        strip.text.x = element_text(size = 20, color = "black"),
      panel.grid = element_blank(),
      panel.spacing = unit(1, "lines"),
      plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0,  # Left margin
                             unit = "cm")) +  # or whatever works best
    labs(title = "C) Area of Activity Space")
  
  return(radar_plot)
}

# Generate the plot
sde_area_radar <- create_sde_area_radar()
print(sde_area_radar)
```

### Activity Plot

```{r}
get_subject_predictions <- function(model) {
  
  # Use the model's original data
  newdata <- model$data
  
  # Get predictions with random effects
  pred_data <- add_predicted_draws(model, newdata = newdata, allow_new_levels = TRUE)
  
  # Get median prediction for each observation
  pred_summary <- pred_data %>%
    group_by(Role, Leave, ParticipantID, isWeekend) %>%
    summarise(median_pred = mean(.prediction), .groups = "drop")
  
  return(pred_summary)
}

morningAct_preds <- get_subject_predictions(model_morningActivityMins_simple) %>%
  mutate(Activity = "Morning")

afternoonAct_preds <- get_subject_predictions(model_afternoonActivityMins_simple) %>%
  mutate(Activity = "Afternoon")

eveningAct_preds <- get_subject_predictions(model_eveningActivityMins_simple) %>%
  mutate(Activity = "Evening")

Act_preds <- rbind(morningAct_preds, afternoonAct_preds, eveningAct_preds) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  )) %>%
  mutate(Activity = as.factor(Activity)) %>%
  mutate(Activity = factor(Activity, levels = c("Morning", "Afternoon", "Evening")))

activity_slope_data <- Act_preds %>%
  filter(isWeekend == "Weekend") %>%
  group_by(ParticipantID, Role, OnLeave) %>%
  summarise(
    Morning = median_pred[Activity == "Morning"],
    Afternoon = median_pred[Activity == "Afternoon"],
    Evening = median_pred[Activity == "Evening"],
    .groups = "drop"
  ) %>%
  pivot_longer(cols = c(Morning, Afternoon, Evening), 
               names_to = "Activity", values_to = "median_pred") %>%
  mutate(Activity = factor(Activity, levels = c("Morning", "Afternoon", "Evening")))

activity_slope_data$group_var <- paste(activity_slope_data$ParticipantID, activity_slope_data$OnLeave, sep = "_")

Act_plot <- ggplot(activity_slope_data, aes(x = Activity, y = median_pred, color = OnLeave, fill = OnLeave, group = ParticipantID)) +
  geom_smooth(aes(group = group_var), se = F, alpha = 0.4, show.legend = T, size = 0.1) +
  geom_point(alpha = 0.8, size = 1, position = position_jitter(width = 0.05)) +
  stat_smooth(aes(group = OnLeave, fill = OnLeave), method = "loess", se = F, alpha = 0.8, show.legend = T, size = 1.5) +
  facet_wrap(~Role) +
  scale_color_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  labs(y = "Activity (minutes)", x = NULL, color = "Leave Status") +
  guides(color = guide_legend(override.aes = list(linetype = 1, size = 2, alpha = 1, fill = NA)), fill = "none"  # don't show fill legend at all
  ) +
  theme_bw() +
  ggtitle('D) Out-of-Home Activity') +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(2, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    panel.spacing = unit(2, "lines"),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))
Act_plot
```

### Spatial Complexity Plot
```{r}
SpatialComplexityData <- rbind(extract_model_predictions_weekend(model_locationVariance_simple, "Location Variance"),
                               extract_model_predictions_weekend(model_maj2min_simple, "Major To Minor Ratio"),
                               extract_model_predictions_weekend(model_entropy_simple, "Spatial Entropy")) %>%
  mutate(Metric = factor(Metric, levels = c("Location Variance", "Spatial Entropy","Major To Minor Ratio")))

# Create combined dot interval plot with different x-axis scales
variance_plot <- ggplot(SpatialComplexityData, aes(y = 0, x = value, color = OnLeave, fill = OnLeave)) +
  stat_dots(quantiles = 150, .width = c(0.5, 0.89), point_interval = "median_qi", dotsize = 1, alpha = 0.9, side = "top") +
  stat_pointinterval(aes(x = value, y = -0.35), data = SpatialComplexityData, .width = c(.66, .95), position = position_dodge(width = 0.4)) +
  facet_grid2(Role ~ Metric, scales = "free", independent = "y", switch = "y") +
  scale_color_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  labs(title = "E) Spatial Complexity", 
       x = "",
       y = "", 
       color = "Leave Status",
       fill = "Leave Status") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 15, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(2, "cm"),
    plot.margin = margin(t = 0.1,
                             r = 0.5, 
                             b = 0.1, 
                             l = 0.1, 
                             unit = "cm"))
```

### Combine the Plots into a Panel
```{r}
try0 <- plot_grid(combined_dot_interval_plot, NULL, HPer_Plot, nrow = 1, rel_widths = c(0.5, 0.1, 0.5))
try1 <- plot_grid(sde_area_radar, NULL, Act_plot, nrow = 1, rel_widths = c(0.5, 0.1, 0.5), align = T)
try2 <- plot_grid(try0, NULL, try1, nrow = 3, rel_heights = c(0.5, 0.05, 0.5))
panel_leavedifference <- plot_grid(try2, NULL, variance_plot, nrow = 3, rel_heights = c(0.6, 0.05, 0.2))

# Create section labels
weekend_label <- ggdraw() + 
  draw_label("Mobility During Weekends", fontface = 'bold', size = 30, hjust = 0.5)

DepressionChangeFull <- plot_grid(rawdepressiondist, NULL, DepressionChangePlot, nrow = 1, rel_widths = c(0.5, 0.1, 0.5))
SleepinessChangeFull <- plot_grid(rawsleepdist, NULL, SleepinessChangePlot, nrow = 1, rel_widths = c(0.5, 0.1, 0.5))

panel_leavedifference <- plot_grid(weekend_label, NULL, try2, NULL, variance_plot, nrow = 5, rel_heights = c(0.08, 0.01, 0.6, 0.05, 0.2))

#ggsave(plot = panel_leavedifference, file = '/work/Paternity-leave/01. BarselProject/niels_geospatial/analysis_code/QuickPlots/FiguresForPaper/panel_leavedifference_weekend.pdf', height = 18, width = 16, dpi = 210)
```








# Depression when not on leave

## Home Time and Depression Score

```{r}
newdata <- modelHomeTimePercent$data

pred_data <- add_predicted_draws(modelHomeTimePercent, newdata = newdata, allow_new_levels = T)

pred_data_subj <- pred_data %>%
  group_by(Leave, d_epdst_sum, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100)

weekday_data <- pred_data_subj %>% #filter(isWeekend == "Weekday") %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

newdata_grid <- expand_grid(
  Role = c("Father", "Mother"),
  Leave = c("Maternity Leave", "Paternity Leave"),
  d_epdst_sum = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18), 
  SleepQuality = 3,
  ParticipantID = NA
)

predictions <- modelHomeTimePercent %>%
  epred_draws(newdata = newdata_grid, re_formula = NA) %>%
  ungroup()

predictions_summary <- predictions %>%
  group_by(Role, Leave, d_epdst_sum) %>%
  summarise(
    mean_home_time = mean(.epred),
    ci_lower_80 = quantile(.epred, 0.055),
    ci_upper_80 = quantile(.epred, 0.945),
    ci_lower_95 = quantile(.epred, 0.975),
    ci_upper_95 = quantile(.epred, 0.025),
    .groups = "drop"
  ) %>%
  arrange(Role, Leave, d_epdst_sum) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))


HomeTimePlot <- ggplot() +
  geom_smooth(aes(x = d_epdst_sum, y = mean_home_time * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_smooth(aes(x = d_epdst_sum, y = ci_lower_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_smooth(aes(x = d_epdst_sum, y = ci_upper_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_point(alpha = 0.9, size = 3, position = position_jitter(width = 0.1), aes(x = as.numeric(d_epdst_sum) - 1, y = mean, color = Role, fill = Role), data = filter(weekday_data, OnLeave == "Not On Leave")) +
  facet_wrap(~Role, ncol = 2) +
  scale_y_continuous(breaks = seq(0, 100, 20), limit = c(0, 100)) +
  scale_x_continuous(breaks = seq(0, 25, 5), limit = c(0, 20)) +
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Edinburgh Postnatal Depression Score", y = "Predicted Home Time (%)") +
  ggtitle('A) Home Time by Postnatal Depression Score') +
  theme_minimal() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, color = "black", hjust = 0.5, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(3, "lines"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = margin(t = 0.1, 
                             r = 0.1,
                             b = 0.1, 
                             l = 0.1, 
                             unit = "cm"))
```

## Posterior Predictions Plot, Depression

```{r}
## Posterior Predictions Plot, Depression
maxdist2 <- as_draws_df(modelmaxdistance)
# Model 2: Home Time Percent
HPer2 <- as_draws_df(modelHomeTimePercent)
# Model 3: Location Variance
LocVar2 <- as_draws_df(modellocationvariance)

# MODEL 1: Max Distance - Distance and Hurdle effects
model1_mother_distance <- maxdist2$`bsp_hu_RoleMother:mod_epdst_sum` + maxdist2$`bsp_hu_RoleMother:mod_epdst_sum:LeavePaternityLeave`
model1_father_distance <- maxdist2$`bsp_RoleFather:mod_epdst_sum`
model1_mother_hurdle <- exp(maxdist2$`bsp_hu_RoleMother:mod_epdst_sum` + maxdist2$`bsp_hu_RoleMother:mod_epdst_sum:LeavePaternityLeave`)
model1_father_hurdle <- exp(maxdist2$`bsp_hu_RoleFather:mod_epdst_sum`)

# MODEL 2: Home Time Percent - Main effect and TOTAL (zoi + coi) effects
model2_mother_distance <- HPer2$`bsp_LeavePaternityLeave:mod_epdst_sum` + HPer2$`bsp_LeavePaternityLeave:mod_epdst_sum:RoleMother`
model2_father_distance <- HPer2$`bsp_LeaveMaternityLeave:mod_epdst_sum`
model2_mother_hurdle <- exp(HPer2$`bsp_zoi_LeavePaternityLeave:mod_epdst_sum` + HPer2$`bsp_zoi_LeavePaternityLeave:mod_epdst_sum:RoleMother` + 
                           HPer2$`bsp_coi_LeavePaternityLeave:mod_epdst_sum` + HPer2$`bsp_coi_LeavePaternityLeave:mod_epdst_sum:RoleMother`)
model2_father_hurdle <- exp(HPer2$`bsp_zoi_LeaveMaternityLeave:mod_epdst_sum` + HPer2$`bsp_coi_LeaveMaternityLeave:mod_epdst_sum`)

# MODEL 3: Location Variance - Distance and Hurdle effects
model3_mother_distance <- LocVar2$`bsp_hu_RoleMother:mod_epdst_sum` + LocVar2$`bsp_hu_RoleMother:mod_epdst_sum:LeavePaternityLeave`
model3_father_distance <- LocVar2$`bsp_RoleFather:mod_epdst_sum`
model3_mother_hurdle <- exp(LocVar2$`bsp_hu_RoleMother:mod_epdst_sum` + LocVar2$`bsp_hu_RoleMother:mod_epdst_sum:LeavePaternityLeave`)
model3_father_hurdle <- exp(LocVar2$`bsp_hu_RoleFather:mod_epdst_sum`)

# Model 1 data
model1_data <- data.frame(
  model = "Max Distance",
  mother_distance = model1_mother_distance,
  father_distance = model1_father_distance,
  mother_hurdle = model1_mother_hurdle,
  father_hurdle = model1_father_hurdle
)

# Model 2 data
model2_data <- data.frame(
  model = "Home Time %",
  mother_distance = model2_mother_distance,
  father_distance = model2_father_distance,
  mother_hurdle = model2_mother_hurdle,
  father_hurdle = model2_father_hurdle
)

# Model 3 data
model3_data <- data.frame(
  model = "Location Variance",
  mother_distance = model3_mother_distance,
  father_distance = model3_father_distance,
  mother_hurdle = model3_mother_hurdle,
  father_hurdle = model3_father_hurdle
)

all_model_data <- rbind(model1_data, model2_data, model3_data)

distance_data <- all_model_data %>%
  select(model, mother_distance, father_distance) %>%
  pivot_longer(cols = c(mother_distance, father_distance),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_distance", "Mother", "Father"),
    parameter_type = "Distance Effect"
  )

hurdle_data <- all_model_data %>%
  select(model, mother_hurdle, father_hurdle) %>%
  pivot_longer(cols = c(mother_hurdle, father_hurdle),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_hurdle", "Mother", "Father"),
    parameter_type = "Hurdle Effect (OR)"
  )

# Calculate summary statistics for dot plots
distance_summary_detailed <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

hurdle_summary_detailed <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

# Distance effects summary
distance_summary <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median_effect = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_negative = mean(effect_size < 0, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)

# Hurdle effects summary
hurdle_summary <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median_or = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_increase_staying = mean(effect_size > 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)


MainEffectsPlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.028,
                      data = distance_data) +
  
  # 95% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = distance_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = distance_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = distance_summary_detailed) +
  
  # Median points - shifted down by 0.1
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = distance_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = distance_summary_detailed) +
  
  # Reference line
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  #scale_fill_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  #scale_color_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Change Per Depression Point", 
       y = "", 
       title = "B) Mobility Response to Depression Symptoms", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(-0.5, 0.7)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

HurdlePlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.05,
                      data = hurdle_data) +
  # 95% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = hurdle_summary_detailed) +
  
  # Median points - shifted down by 0.15
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = hurdle_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = hurdle_summary_detailed) +
  
  # Reference line (OR = 1)
  geom_vline(xintercept = 1, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Odds Ratio Per Depression Point", 
       y = "", 
       title = "C) Odds of Staying Home by Depression Level", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(0.5, 2)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.8),
    legend.key.size = unit(2, "lines"),
    legend.text = element_text(size = 18),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

ChangeForDepression <- plot_grid(MainEffectsPlot, NULL, HurdlePlot, ncol = 3, rel_widths = c(0.5, 0.02, 0.5))


notonleave_label <- ggdraw() + 
  draw_label("Depression Results When Not Leave", fontface = 'bold', size = 30, hjust = 0.5)

DepressionPlots <- plot_grid(notonleave_label, NULL, HomeTimePlot, NULL, ChangeForDepression, nrow = 5, rel_heights = c(0.08, 0.01, 0.5, 0.1, 0.5))

#ggsave(plot = DepressionPlots, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "DepressionPlots_NotOnLeave.pdf"), height = 14, width = 15)
```

## Home Time and Sleep Quality

```{r}
newdata <- d_GPS %>%
  group_by(ParticipantID, Role, Leave, SleepQuality) %>%
  summarise(n = n()) %>%
  mutate(d_epdst_sum = median(as.numeric(d_GPS$d_epdst_sum))) %>%
  filter(SleepQuality %in% c('1', '2', '3', '4', '5')) %>%
  mutate(SleepQuality = factor(SleepQuality, levels = c('1', '2', '3', '4', '5'))) %>%
  mutate(SleepQuality = as.ordered(SleepQuality)) %>%
  print(n = 50)

pred_data <- add_predicted_draws(modelHomeTimePercent, newdata = newdata, allow_new_levels = T)

pred_data_subj <- pred_data %>%
  group_by(Leave, d_epdst_sum, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100)

pred_data_subj <- pred_data %>%
  group_by(Leave, SleepQuality, Role, ParticipantID) %>%
  summarise(mean = mean(.prediction) * 100) %>%
  mutate(SleepQuality_factor = factor(SleepQuality, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))

weekday_data <- pred_data_subj %>% #filter(isWeekend == "Weekday") %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ))

newdata_grid <- expand_grid(
  Role = c("Father", "Mother"),
  Leave = c("Maternity Leave", "Paternity Leave"),
  d_epdst_sum = c(5), 
  SleepQuality = c(1, 2, 3, 4, 5),
  ParticipantID = NA
)

predictions <- modelHomeTimePercent %>%
  epred_draws(newdata = newdata_grid, re_formula = NA) %>%
  ungroup()

predictions_summary <- predictions %>%
  group_by(Role, Leave, SleepQuality) %>%
  summarise(
    mean_home_time = mean(.epred),
    ci_lower_80 = quantile(.epred, 0.055),
    ci_upper_80 = quantile(.epred, 0.945),
    ci_lower_95 = quantile(.epred, 0.975),
    ci_upper_95 = quantile(.epred, 0.025),
    .groups = "drop"
  ) %>%
  arrange(Role, Leave, SleepQuality) %>%
  mutate(OnLeave = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave",
  ),
  SleepQuality_factor = factor(SleepQuality, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))
  
HomeTimeSleepPlot <- ggplot() +
  geom_smooth(aes(x = SleepQuality, y = mean_home_time * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_smooth(aes(x = SleepQuality, y = ci_lower_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_smooth(aes(x = SleepQuality, y = ci_upper_80 * 100, color = Role), se = F, formula = y ~ splines::ns(x, df = 3), method = "lm", linetype = "dashed", data = filter(predictions_summary, OnLeave == "Not On Leave")) +
  geom_point(alpha = 0.9, size = 3, position = position_jitter(width = 0.1), aes(x = as.numeric(SleepQuality), y = mean, color = Role, fill = Role), data = filter(weekday_data, OnLeave == "Not On Leave")) +
  facet_wrap(~Role, ncol = 2) +
  scale_y_continuous(breaks = seq(0, 100, 20), limit = c(0, 100)) +
  scale_x_continuous(breaks = seq(1, 5, 1), limit = c(0, 5), labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")) +
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Reported Sleep Quality", y = "Predicted Home Time (%)") +
  ggtitle('A) Home Time by Daily Sleep Quality') +
  theme_minimal() +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, color = "black", hjust = 0.5, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(3, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))
```

## Posterior Predictions Plot, Sleep

```{r}
maxdist2

## Posterior Predictions Plot, Depression
maxdist2 <- as_draws_df(modelmaxdistance)
# Model 2: Home Time Percent
HPer2 <- as_draws_df(modelHomeTimePercent)
# Model 3: Location Variance
LocVar2 <- as_draws_df(modellocationvariance)

# MODEL 1: Max Distance - Distance and Hurdle effects
model1_mother_distance <- maxdist2$`bsp_hu_RoleMother:moSleepQuality` + maxdist2$`bsp_hu_RoleMother:moSleepQuality:LeavePaternityLeave`
model1_father_distance <- maxdist2$`bsp_RoleFather:moSleepQuality`
model1_mother_hurdle <- exp(maxdist2$`bsp_hu_RoleMother:moSleepQuality` + maxdist2$`bsp_hu_RoleMother:moSleepQuality:LeavePaternityLeave`)
model1_father_hurdle <- exp(maxdist2$`bsp_hu_RoleFather:moSleepQuality`)

# MODEL 2: Home Time Percent - Main effect and TOTAL (zoi + coi) effects
model2_mother_distance <- HPer2$`bsp_LeavePaternityLeave:moSleepQuality` + HPer2$`bsp_LeavePaternityLeave:moSleepQuality:RoleMother`
model2_father_distance <- HPer2$`bsp_LeaveMaternityLeave:moSleepQuality`
model2_mother_hurdle <- exp(HPer2$`bsp_zoi_LeavePaternityLeave:moSleepQuality` + HPer2$`bsp_zoi_LeavePaternityLeave:moSleepQuality:RoleMother` + 
                           HPer2$`bsp_coi_LeavePaternityLeave:moSleepQuality` + HPer2$`bsp_coi_LeavePaternityLeave:moSleepQuality:RoleMother`)
model2_father_hurdle <- exp(HPer2$`bsp_zoi_LeaveMaternityLeave:moSleepQuality` + HPer2$`bsp_coi_LeaveMaternityLeave:moSleepQuality`)

# MODEL 3: Location Variance - Distance and Hurdle effects
model3_mother_distance <- LocVar2$`bsp_hu_RoleMother:moSleepQuality` + LocVar2$`bsp_hu_RoleMother:moSleepQuality:LeavePaternityLeave`
model3_father_distance <- LocVar2$`bsp_RoleFather:moSleepQuality`
model3_mother_hurdle <- exp(LocVar2$`bsp_hu_RoleMother:moSleepQuality` + LocVar2$`bsp_hu_RoleMother:moSleepQuality:LeavePaternityLeave`)
model3_father_hurdle <- exp(LocVar2$`bsp_hu_RoleFather:moSleepQuality`)

# Model 1 data
model1_data <- data.frame(
  model = "Max Distance",
  mother_distance = model1_mother_distance,
  father_distance = model1_father_distance,
  mother_hurdle = model1_mother_hurdle,
  father_hurdle = model1_father_hurdle
)

# Model 2 data
model2_data <- data.frame(
  model = "Home Time %",
  mother_distance = model2_mother_distance,
  father_distance = model2_father_distance,
  mother_hurdle = model2_mother_hurdle,
  father_hurdle = model2_father_hurdle
)

# Model 3 data
model3_data <- data.frame(
  model = "Location Variance",
  mother_distance = model3_mother_distance,
  father_distance = model3_father_distance,
  mother_hurdle = model3_mother_hurdle,
  father_hurdle = model3_father_hurdle
)

all_model_data <- rbind(model1_data, model2_data, model3_data)

distance_data <- all_model_data %>%
  select(model, mother_distance, father_distance) %>%
  pivot_longer(cols = c(mother_distance, father_distance),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_distance", "Mother", "Father"),
    parameter_type = "Distance Effect"
  )

hurdle_data <- all_model_data %>%
  select(model, mother_hurdle, father_hurdle) %>%
  pivot_longer(cols = c(mother_hurdle, father_hurdle),
               names_to = "effect_type", values_to = "effect_size") %>%
  filter(!is.na(effect_size)) %>%
  mutate(
    role = ifelse(effect_type == "mother_hurdle", "Mother", "Father"),
    parameter_type = "Hurdle Effect (OR)"
  )

# Calculate summary statistics for dot plots
distance_summary_detailed <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

hurdle_summary_detailed <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median = median(effect_size, na.rm = TRUE),
    mean = mean(effect_size, na.rm = TRUE),
    ci_lower_50 = quantile(effect_size, 0.25, na.rm = TRUE),
    ci_upper_50 = quantile(effect_size, 0.75, na.rm = TRUE),
    ci_lower_80 = quantile(effect_size, 0.10, na.rm = TRUE),
    ci_upper_80 = quantile(effect_size, 0.90, na.rm = TRUE),
    ci_lower_95 = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper_95 = quantile(effect_size, 0.975, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(model_role = paste0(model, " (", role, ")"))

# Distance effects summary
distance_summary <- distance_data %>%
  group_by(model, role) %>%
  summarise(
    median_effect = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_negative = mean(effect_size < 0, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)

# Hurdle effects summary
hurdle_summary <- hurdle_data %>%
  group_by(model, role) %>%
  summarise(
    median_or = median(effect_size, na.rm = TRUE),
    ci_lower = quantile(effect_size, 0.025, na.rm = TRUE),
    ci_upper = quantile(effect_size, 0.975, na.rm = TRUE),
    prob_increase_staying = mean(effect_size > 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(model, role)


MainEffectsPlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.1,
                      data = distance_data) +
  
  # 95% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = distance_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = distance_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.1
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = distance_summary_detailed) +
  
  # Median points - shifted down by 0.1
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = distance_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = distance_summary_detailed) +
  
  # Reference line
  geom_vline(xintercept = 0, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  #scale_fill_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  #scale_color_manual(values = c("Mother" = "#D95F02", "Father" = "#009E73")) +
  
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Change Per Sleep Category", 
       y = "", 
       title = "B) Mobility Response to Sleep Quality", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(-2, 3)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    #axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "none",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    #panel.grid.major.x= element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

HurdlePlot <- ggplot() +
  # Ridge distributions
  geom_density_ridges(aes(x = effect_size, y = model, fill = role), 
                      alpha = 0.8, scale = 0.5, rel_min_height = 0.015, bandwidth = 0.07,
                      data = hurdle_data) +
  # 95% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_95, xend = ci_upper_95, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role), 
               size = 1, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 80% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_80, xend = ci_upper_80, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                   color = role),  
               size = 2, alpha = 0.8, data = hurdle_summary_detailed) +
  
  # 50% CI segments - shifted down by 0.15
  geom_segment(aes(x = ci_lower_50, xend = ci_upper_50, 
                   y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   yend = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15, 
                   color = role),  
               size = 3, data = hurdle_summary_detailed) +
  
  # Median points - shifted down by 0.15
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 3, color = "black", stroke = 1.5, data = hurdle_summary_detailed) +
  geom_point(aes(x = median,
                 y = as.numeric(as.factor(model)) + ifelse(role == "Mother", -0.05, 0.05) - 0.15,
                 color = role), 
             size = 2, data = hurdle_summary_detailed) +
  
  # Reference line (OR = 1)
  geom_vline(xintercept = 1, linetype = "dashed", color = "black", size = 1) +
  
  # Scales and aesthetics
  scale_color_okabe_ito() +
  scale_fill_okabe_ito() +
  labs(x = "Odds Ratio Per Sleep Point", 
       y = "", 
       title = "C) Odds of Staying Home by Sleep Quality", 
       fill = "Role") +
  
  guides(color = "none") +  # Hide color legend since fill legend shows the same info
  xlim(c(0.2, 3)) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.8),
    legend.key.size = unit(2, "lines"),
    legend.text = element_text(size = 18),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    panel.border = element_blank(),
    strip.background = element_rect(color="white", fill="white", linewidth=1.5, linetype="solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    panel.spacing = unit(2, "lines"),
    panel.grid.minor.x = element_blank(),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

ChangeForSleep <- plot_grid(MainEffectsPlot, NULL, HurdlePlot, ncol = 3, rel_widths = c(0.5, 0.02, 0.5))
ChangeForSleep

notonleave_label <- ggdraw() + 
  draw_label("Sleep Results When Not Leave", fontface = 'bold', size = 30, hjust = 0.5)

SleepPlots <- plot_grid(notonleave_label, NULL, HomeTimeSleepPlot, NULL, ChangeForSleep, nrow = 5, rel_heights = c(0.08, 0.01, 0.5, 0.1, 0.5))

#ggsave(plot = SleepPlots, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "SleepPlotsNotOnLeave.pdf"), height = 14, width = 16)
```

# Run Model on Subset with Participants in both leave periods

## Depression

```{r}
d_GPS_both_timepoints <- d_GPS %>%
  filter(ParticipantID %in% participants_both)

formula_depression <- bf(d_epdst_sum ~ 1 + Role + Role:Leave + (Leave | gr(ParticipantID, by = Role)))

priors_depression <- c(
  prior(normal(0, 5), class = Intercept),
  prior(normal(0, 2), class = b),
  prior(normal(0, 2), class = sd, group = ParticipantID),
  prior(lkj(2), class = cor, group = ParticipantID)
)

mediator_depression_ordinal_bothleaveparticipants <- brm(
  formula_depression,
  family = cumulative("logit"),
  data = d_GPS_depression,
  prior = priors_depression,
  cores = 64,
  chains = 2,
  warmup = 500,
  iter = 5000,
  control = list(adapt_delta = 0.95),
  backend = 'cmdstan'
)

pp_check(mediator_depression_ordinal_bothleaveparticipants, ndraws = 100)
```

```{r}
mediator_depression_ordinal_bothleaveparticipants <- readRDS(here("analysis_code", "models", "mediator_depression_ordinal_bothleaveparticipants.rds"))

newdata <- expand_grid(
    Role = c("Mother", "Father"),
    Leave = c("Maternity Leave", "Paternity Leave"),
    isWeekend = "Weekday",
    ParticipantID = unique(d_GPS$ParticipantID)
  )

predictions <- newdata %>%
  add_predicted_draws(mediator_depression_ordinal_bothleaveparticipants, ndraws = 3000, re_formula = NA)  %>%
  mutate(Leave_Clean = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave"))
  
prob_summary <- predictions %>%
  filter(!is.na(.prediction)) %>%
  group_by(Role, Leave_Clean) %>%
  count(.prediction = as.numeric(.prediction)) %>%
  mutate(prob = n / sum(n)) %>%  
  select(-n)
  
prob_differences <- prob_summary %>%
    pivot_wider(names_from = Leave_Clean, values_from = prob, values_fill = 0) %>%
    mutate(
      difference = `On Leave` - `Not On Leave`,
      change_type = ifelse(difference > 0, "Increase During Leave", "Decrease During Leave")
    ) %>%
    mutate(difference = difference * 100)

DepressionChangePlot <- ggplot(aes(x = .prediction - 1, y = difference, fill = change_type), data = prob_differences, alpha = 0.5) +
    geom_col(color = "black", alpha = 0.9) +
    geom_hline(yintercept = 0, color = "black") +
    scale_x_continuous(breaks = seq(0, 21, by = 3)) +
    scale_y_continuous(breaks = seq(-10, 10, by = 2)) +
    facet_wrap(~Role) +
  scale_fill_manual(values = c("Increase During Leave" = "#00468b", "Decrease During Leave" = "#D73027"), name = "Probability Change") +
    theme_bw() +
    labs(title = "Depression Scores Difference", x = "Edinburgh Postnatal Depression Score", y = "Difference in Ordinal Probability (%)\n(On Leave - Not On Leave)") +
    theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    #panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(1, "cm"),
    plot.margin = margin(t = 0.1,  
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))

predictions_summary <- predictions %>%
  group_by(Role, Leave_Clean) %>%
  count(.prediction = as.numeric(.prediction)) %>%
  mutate(proportion = n / sum(n))

rawdepressiondist <- predictions_summary %>%
  ggplot(aes(x = .prediction - 1, y = proportion * 100, fill = Leave_Clean)) +
  geom_col(position = "dodge", alpha = 0.9, color = "black") +
  facet_wrap(~Role) +
  scale_fill_manual(values = c("Not On Leave" = "#f39b7f", "On Leave" = "#3c5488")) +
  labs(title = "Depression Score Distributions",
       x = "Edinburgh Postnatal Depression Score",
       y = "Proportion of Sample (%)",
       fill = NULL) +
  theme_bw() +
  scale_x_continuous(breaks = seq(0, 18, 3)) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    axis.ticks.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    #panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(1, "cm"),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))


mediator_depression_ordinal_bothleaveparticipants$data %>%
  group_by(Role) %>%
  summarise(count = n_distinct(ParticipantID))

bothleaveparticipants_label <- ggdraw() + 
  draw_label("Depression for Parents Measured at Both Leave Periods \nSubsample Included 35 Fathers, 31 Mothers", fontface = 'bold', size = 25, hjust = 0.5)

DepressionChangeFull <- plot_grid(bothleaveparticipants_label, NULL, rawdepressiondist, NULL, DepressionChangePlot, nrow = 5, rel_heights = c(0.08, 0.07, 0.5, 0.1, 0.5))
DepressionChangeFull

#ggsave(plot = DepressionChangeFull, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "DepressionChangeFullBothLeave.pdf"), height = 14, width = 12)
```

## Sleep

```{r}
formula_sleep <- bf(
  SleepQuality_int ~ 1 + Role + Role:Leave + Role:Leave:isWeekend + (Leave | gr(ParticipantID, by = Role))
)

priors_sleep <- c(
  prior(normal(0, 5), class = Intercept),
  prior(normal(0, 2), class = b),
  prior(normal(0, 2), class = sd, group = ParticipantID),
  prior(lkj(2), class = cor, group = ParticipantID)
)

mediator_sleep_bothleaveparticipants <- brm(
  formula_sleep,
  family = cumulative("logit"),
  prior = priors_sleep,
  data = d_GPS_both_timepoints,
  cores = 64,
  chains = 2,
  warmup = 500,
  iter = 2000,
  control = list(adapt_delta = 0.95),
  backend = 'cmdstan'
)

pp_check(mediator_sleep_bothleaveparticipants, ndraws = 100)
```


```{r}
mediator_sleep_bothleaveparticipants <- readRDS(here("analysis_code", "models", "mediator_sleep_bothleaveparticipants.rds"))

newdata <- expand_grid(
    Role = c("Mother", "Father"),
    Leave = c("Maternity Leave", "Paternity Leave"),
    isWeekend = "Weekday",
    ParticipantID = unique(d_GPS$ParticipantID)
  )
  
predictions <- newdata %>%
    add_predicted_draws(mediator_sleep_bothleaveparticipants, ndraws = 3000, re_formula = NA)  %>%
  mutate(Leave_Clean = case_when(
    Leave == "Paternity Leave" & Role == "Father" ~ "On Leave",
    Leave == "Maternity Leave" & Role == "Mother" ~ "On Leave",
    Leave == "Paternity Leave" & Role == "Mother" ~ "Not On Leave",
    Leave == "Maternity Leave" & Role == "Father" ~ "Not On Leave"))

prob_summary <- predictions %>%
  filter(!is.na(.prediction)) %>%
  group_by(Role, Leave_Clean) %>%
  count(.prediction = as.numeric(.prediction)) %>%
  mutate(prob = n / sum(n)) %>% 
  select(-n)

prob_differences <- prob_summary %>%
  pivot_wider(names_from = Leave_Clean, values_from = prob, values_fill = 0) %>%
  mutate(
    difference = `On Leave` - `Not On Leave`,
    change_type = ifelse(difference > 0, "Increase During Leave", "Decrease During Leave")
  ) %>%
  mutate(difference = difference * 100,
         SleepQuality_factor = factor(.prediction, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))
  
SleepinessChangePlot <- ggplot(aes(x = SleepQuality_factor, y = difference, fill = change_type), data = prob_differences, alpha = 0.7) +
    geom_col(color = "black", alpha = 0.9) +
    geom_hline(yintercept = 0, color = "black") +
    scale_y_continuous(breaks = seq(-30, 25, by = 5)) +
    facet_wrap(~Role) +
  scale_fill_manual(values = c("Increase During Leave" = "#00468b", "Decrease During Leave" = "#D73027"), name = "Probability Change") +
    theme_bw() +
    labs(title = "Daily Sleep Quality Difference", x = "Daily Reported Sleep Quality", y = "Difference in Ordinal Probability (%)\n(On Leave - Not On Leave)") +
    theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    axis.ticks.y = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(1, "cm"),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

predictions_summary <- predictions %>%
  group_by(Role, Leave_Clean) %>%
  count(.prediction = as.numeric(.prediction)) %>%
  mutate(proportion = n / sum(n)) %>%
  mutate(SleepQuality_factor = factor(.prediction, levels = 1:5, 
                                  labels = c("V. Poor", "Poor", "Fair", "Good", "V. Good")))

rawsleepdist <- predictions_summary %>%
  ggplot(aes(x = SleepQuality_factor, y = proportion * 100, fill = Leave_Clean)) +
  geom_col(position = "dodge", alpha = 0.9, color = "black") +
  facet_wrap(~Role) +
  scale_fill_manual(values = c("Not On Leave" = "#f39b7f", "On Leave" = "#3c5488")) +
  labs(title = "Daily Sleep Quality Distributions",
       x = "Daily Reported Sleep Quality",
       y = "Proportion of Sample (%)",
       fill = NULL) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_text(size = 15, color = "black"),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 20, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    #panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(1, "cm"),
    plot.margin = margin(t = 0.1,
                             r = 0.1,
                             b = 0.1,
                             l = 0.1,
                             unit = "cm"))

mediator_sleep_bothleaveparticipants$data %>%
  group_by(Role) %>%
  summarise(count = n_distinct(ParticipantID))

bothleaveparticipants_label <- ggdraw() + 
  draw_label("Sleep Quality for Parents Measured at Both Leave Periods \nSubsample Included 35 Fathers, 31 Mothers", fontface = 'bold', size = 25, hjust = 0.5)

SleepinessChangeFull <- plot_grid(bothleaveparticipants_label, NULL, rawsleepdist, NULL, SleepinessChangePlot, nrow = 5, rel_heights = c(0.08, 0.07, 0.5, 0.1, 0.5))
SleepinessChangeFull

#ggsave(plot = SleepinessChangeFull, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "SleepinessChangeFullBothLeave.pdf"), height = 14, width = 12)
```

# Linear Depression Model
```{r}
formula_depression <- bf(d_epdst_sum ~ 1 + Role + Role:Leave + (Leave | gr(ParticipantID, by = Role)))

priors_depression <- c(
  prior(normal(4, 5), class = Intercept),
  prior(normal(0, 2), class = b),
  prior(normal(0, 2), class = sd, group = ParticipantID),
  prior(lkj(2), class = cor, group = ParticipantID)
)

mediator_depression_linear <- brm(
  formula_depression,
  family = gaussian(),
  data = d_GPS_depression,
  prior = priors_depression,
  cores = 64,
  chains = 2,
  warmup = 2000,
  iter = 5000,
  control = list(adapt_delta = 0.9999, max_treedepth = 20),
  backend = 'cmdstan'
)

pp_check(mediator_depression_linear, ndraws = 100)
```


```{r}
mediator_depression_linear <- readRDS(here("analysis_code", "models", "mediator_depression_linear.rds"))

posterior <- as_draws_df(mediator_depression_linear)

paternityleavefathers <- as_tibble(posterior$b_Intercept + posterior$`b_RoleFather:LeavePaternityLeave`) %>%
  mutate(Role = "Father") %>%
  mutate(OnLeave = "On Leave")

maternityleavefathers <- as_tibble(posterior$b_Intercept) %>%
  mutate(Role = "Father") %>%
  mutate(OnLeave = "Not On Leave")

maternityleavemothers <- as_tibble(posterior$b_Intercept + posterior$b_RoleMother) %>%
  mutate(Role = "Mother") %>%
  mutate(OnLeave = "On Leave")

paternityleavemothers <- as_tibble(posterior$b_Intercept + posterior$b_RoleMother + posterior$`b_RoleMother:LeavePaternityLeave`) %>%
  mutate(Role = "Mother") %>%
  mutate(OnLeave = "Not On Leave")

lineardepressionmodel <- rbind(paternityleavefathers, maternityleavefathers,  maternityleavemothers, paternityleavemothers)

linearplot <- ggplot(lineardepressionmodel) +
  geom_histogram(aes(x = value, fill = OnLeave), alpha = 0.7, color = "black") +
  facet_wrap(~Role, scale = "fixed") +
  scale_fill_manual(values = c("On Leave" = "#3c5488", "Not On Leave" = "#f39b7f")) +
  xlab('Edinburgh Postnatal Depression Scores') +
  ylab(' ') +
  ggtitle('Linear Model Predictions for Depression Scores') +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20, face = "bold", color = "black"), 
    axis.text.x = element_text(size = 15, color = "black"),
    axis.title.x = element_text(size = 15, color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_text(size = 15, color = "black"),
    legend.title = element_blank(),
    legend.position = "top",
    legend.key.size = unit(1, "lines"),
    legend.text = element_text(size = 15),
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    strip.background = element_rect(color = "white", fill = "white", linewidth = 1.5, linetype = "solid"),
    strip.text.x = element_text(size = 15, color = "black"),
    strip.text.y = element_text(size = 15, color = "black"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.border = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(2, "cm"),
    plot.margin = margin(t = 0.1,  # Top margin
                             r = 0.1,  # Right margin
                             b = 0.1,  # Bottom margin
                             l = 0.1,  # Left margin
                             unit = "cm"))

#ggsave(plot = linearplot, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "SupplementaryLinearModelPlot.pdf"), height = 7, width = 8)
```

# Posterior Predictive Check

```{r}
create_posterior_check <- function(model, ndraws = 100, resp = NULL, title = title, xlow = NULL, xhigh = NULL) {
  
  if (is.null(title)) {
    title <- title
  }
  
  if (!is.null(resp)) {
    # For multivariate models
    plot <- pp_check(model, ndraws = ndraws, resp = resp) +
      ggtitle(title) +
      theme_bw() +
      theme(
        plot.title = element_text(hjust = 0.5, size = 16),
        axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.position = "none"
      )
  } else {
    # For single response models
    plot <- pp_check(model, ndraws = ndraws) +
      ggtitle(title) +
      xlim(c(xlow, xhigh)) +
      theme_bw() +
      theme(
        plot.title = element_text(hjust = 0.5, size = 16),
        axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        legend.position = "none"
      )
  }
  
  return(plot)
}

# RQ1 Models
pp_MaxDist <- create_posterior_check(model_maxDistanceFromHomeKm_simple, xlow = 0, xhigh = 50, title = "Max Distance")
pp_HPer <- create_posterior_check(modelHomeTimePercent_simple, xlow = 0, xhigh = 1, title = "Home Time Percentage")
pp_maj2min <- create_posterior_check(model_maj2min_simple, xlow = -3, xhigh = 30, title = "Major to Minor Ratio")
pp_entropy <- create_posterior_check(model_entropy_simple, xlow = 0, xhigh = 1, title = "Spatial Entropy")
pp_SDE <- create_posterior_check(model_SDE_simple, xlow = 0, xhigh = 10, title = "Area of Activity Space")
pp_radius <- create_posterior_check(model_radiusOfGyrationKm_simple, xlow = 0, xhigh = 5, title = "Gyration Radius")
pp_LocVar <- create_posterior_check(model_locationVariance_simple, xlow = 0, xhigh = 10, title = "Location Variance")

# RQ2 Models
pp_sleep_mediator <- create_posterior_check(mediator_sleep, xlow = 0, xhigh = 5.8, title = "Sleep Quality")
pp_depression_mediator <- create_posterior_check(mediator_depression_ordinal, xlow = -4, xhigh = 22, title = "Postnatal Depression Scores")

# RQ3 Models
pp_Hperdep <- create_posterior_check(modelHomeTimePercent, xlow = -0.25, xhigh = 1.25, title = "Home Time Percentage, Depression")
pp_dist <- create_posterior_check(modelmaxdistance, xlow = -0.5, xhigh = 50, title = "Max Distance, Depression")
pp_locvardep <- create_posterior_check(modellocationvariance, xlow = -0.5, xhigh = 20, title = "Location Variance, Depression")

RQ1_label <- ggdraw() + 
  draw_label("RQ1 Models", fontface = 'bold', size = 20, hjust = 0.5)

RQ2_label <- ggdraw() + 
  draw_label("RQ2 Models", fontface = 'bold', size = 20, hjust = 0.5)

RQ3_label <- ggdraw() + 
  draw_label("RQ3 Models", fontface = 'bold', size = 20, hjust = 0.5)

pp_checks <- plot_grid(RQ1_label, 
                       plot_grid(pp_MaxDist, pp_HPer), 
                       plot_grid(pp_maj2min, pp_entropy), 
                       plot_grid(pp_radius, pp_LocVar), 
                       RQ2_label,
                       plot_grid(pp_sleep_mediator, pp_depression_mediator),
                       RQ3_label,
                       plot_grid(pp_Hperdep, pp_locvardep, pp_dist, nrow = 1),
                       nrow = 8,
                       rel_heights = c(0.05, 0.2, 0.2, 0.2, 0.05, 0.2, 0.05, 0.2)
                       )

ggsave(plot = pp_checks, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "pp_checks.pdf"), height = 15, width = 12)
         
# Extract posterior samples
posterior <- as.array(modelHomeTimePercent)

MCMCTracePlot <- mcmc_trace(posterior, 
           pars = c("b_RoleFather", 
                    "b_RoleMother",
                    "b_RoleMother:LeavePaternityLeave",
                    "b_RoleFather:LeavePaternityLeave",
                    "bsp_coi_LeavePaternityLeave:mod_epdst_sum",
                    "bsp_coi_LeaveMaternityLeave:mod_epdst_sum:RoleMother"
                    ),
           facet_args = list(nrow = 3, labeller = as_labeller(c("b_RoleFather" = "Father, Maternity Leave",
                                                      "b_RoleMother" = "Mother, Maternity Leave",
                                                      "b_RoleMother:LeavePaternityLeave" = "Mother, Paternity Leave",
                                                      "b_RoleFather:LeavePaternityLeave" = "Father, Paternity Leave",
                                                      "bsp_coi_LeavePaternityLeave:mod_epdst_sum" = "Father, StayHome",
                                                      "bsp_coi_LeaveMaternityLeave:mod_epdst_sum:RoleMother" = "Mother, StayHome")))) +
  scale_color_manual(values = c("#e64b35", "#4dbbd5", "#00a087", "#f39b7f")) +
  xlab('Iterations') +
  ylab('Parameter Value') +
  theme_minimal() +
  theme(
      plot.title = element_text(hjust = 0.5, size = 25, margin = margin(b = 0)),
      axis.text.x = element_text(size = 20, color = "black"),
      axis.title.x = element_text(size = 20), 
      axis.text.y = element_text(size = 20, color = "black"),
      axis.title.y = element_text(size = 20), 
      axis.ticks = element_blank(),
      legend.position = "none",
      legend.text = element_text(size = 20),
      legend.title = element_text(size = 20),
      axis.line.y = element_blank(),
      axis.line.x = element_blank(),
      panel.grid.minor = element_blank(),
      panel.spacing = unit(1, "cm"),
      strip.background = element_rect(
        color = "white", 
        fill = "white", 
        linewidth = 1.5, 
        linetype = "solid"
      ),
      strip.text.x = element_text(size = 20, color = "black")
    )

#ggsave(plot = MCMCTracePlot, file = here("analysis_code", "QuickPlots", "FiguresForPaper", "MCMCTracePlot.pdf", height = 15, width = 15)
```

# Data Anonymization
```{r}
glimpse(d_GPS)

anonymize_gps_data <- function(original_data, seed = 42) {
  
  # Set seed for reproducibility
  set.seed(seed)
  
  participants <- unique(original_data$ParticipantID)
  anonymized_data <- list()
  
  for (participant in participants) {
    participant_data <- original_data %>% filter(ParticipantID == participant)
    new_participant_id <- sprintf("P%03d", which(participants == participant))
    n_rows <- nrow(participant_data)
    
    anon_participant <- participant_data
    
    # 1. Change identifiers
    anon_participant$ParticipantID <- new_participant_id
    anon_participant$CoupleID <- paste0("C", sprintf("%03d", ceiling(which(participants == participant)/2)))
    
    # Remove or anonymize user ID
    anon_participant$userId <- paste0("user_", new_participant_id)
    
    # 2. Temporal anonymization - shift dates by random amount (30 days)
    if ("date" %in% colnames(anon_participant)) {
      date_shift <- sample(-30:30, 1)
      anon_participant$date <- as.character(as.Date(anon_participant$date) + date_shift)
      
      # Update other date fields consistently
      if ("Date" %in% colnames(anon_participant)) {
        anon_participant$Date <- format(as.Date(anon_participant$date), "%d/%m/%Y")
      }
      if ("DateEnrolled" %in% colnames(anon_participant)) {
        anon_participant$DateEnrolled <- format(as.Date(anon_participant$date[1]), "%d/%m/%Y")
      }
    }
    
    # 3. Location anonymization - remove precise coordinates
    if ("Location" %in% colnames(anon_participant)) {
      anon_participant$Location <- NA  # Remove precise GPS coordinates
    }
    
    # 4. Apply noise to mobility metrics
    mobility_cols <- c("radiusOfGyrationKm", "activitySpaceAreaKm2", "locationVariance",
                       "SDE", "maxDistanceFromHomeKm", "totalDistanceKm", 
                       "activeTravelDistanceKm", "passiveTravelDistanceKm",
                       "avgMoveDistanceKm")
    
    for (col in mobility_cols) {
      if (!(col %in% colnames(anon_participant))) next
      
      non_na_indices <- which(!is.na(anon_participant[[col]]))
      
      if (length(non_na_indices) > 0) {
        col_values <- anon_participant[[col]][non_na_indices]
        col_sd <- sd(col_values, na.rm = TRUE)
        
        if (is.na(col_sd) || col_sd == 0) next
        
        # Apply noise - 3% of standard deviation for spatial measures
        noise_factor <- 0.03
        anon_participant[[col]][non_na_indices] <- pmax(0, # Ensure non-negative values
          col_values + rnorm(length(non_na_indices), 0, col_sd * noise_factor))
      }
    }
    
    # 5. Apply smaller noise to percentage and ratio measures
    percentage_cols <- c("homeTimePercent", "travelTimePercent", "totalOHTimePercent",
                         "stayOHTimePercent", "revistedLS", "avgRevistedLS")
    
    for (col in percentage_cols) {
      if (!(col %in% colnames(anon_participant))) next
      
      non_na_indices <- which(!is.na(anon_participant[[col]]))
      
      if (length(non_na_indices) > 0) {
        col_values <- anon_participant[[col]][non_na_indices]
        col_sd <- sd(col_values, na.rm = TRUE)
        
        if (is.na(col_sd) || col_sd == 0) next
        
        # Smaller noise for percentages - 1% of standard deviation
        noise_factor <- 0.01
        noisy_values <- col_values + rnorm(length(non_na_indices), 0, col_sd * noise_factor)
        
        # Keep percentages within reasonable bounds
        if (grepl("Percent", col)) {
          noisy_values <- pmax(0, pmin(100, noisy_values))
        }
        
        anon_participant[[col]][non_na_indices] <- noisy_values
      }
    }
    
    # 6. Apply noise to count measures
    count_cols <- c("pointCount", "stayCount", "oohStays", "moveCount", 
                    "homeCount", "numLocations", "numUniqueLocations")
    
    for (col in count_cols) {
      if (!(col %in% colnames(anon_participant))) next
      
      non_na_indices <- which(!is.na(anon_participant[[col]]))
      
      if (length(non_na_indices) > 0) {
        # For counts, add small random integer noise
        original_values <- anon_participant[[col]][non_na_indices]
        noise <- sample(-2:2, length(non_na_indices), replace = TRUE, 
                       prob = c(0.1, 0.2, 0.4, 0.2, 0.1))  # Bias toward no change
        
        anon_participant[[col]][non_na_indices] <- pmax(0, original_values + noise)
      }
    }
    
    # 7. Apply noise to sleep and wellness measures
    wellness_cols <- c("SleepQuality_int", "ParticipantChecksBaby", "PartnerChecksBaby")
    
    for (col in wellness_cols) {
      if (!(col %in% colnames(anon_participant))) next
      
      non_na_indices <- which(!is.na(anon_participant[[col]]))
      
      if (length(non_na_indices) > 0) {
        original_values <- anon_participant[[col]][non_na_indices]
        # Small random adjustments
        noise <- sample(-1:1, length(non_na_indices), replace = TRUE,
                       prob = c(0.2, 0.6, 0.2))
        
        anon_participant[[col]][non_na_indices] <- pmax(0, original_values + noise)
      }
    }
    
    # 8. Shuffle small percentage of study days (optional temporal distortion)
    if ("studyDay" %in% colnames(anon_participant) && n_rows >= 5) {
      n_to_shuffle <- max(1, round(n_rows * 0.10))  # 10% shuffle rate
      shuffle_indices <- sample(1:n_rows, n_to_shuffle)
      
      available_days <- unique(anon_participant$studyDay)
      
      for (idx in shuffle_indices) {
        anon_participant$studyDay[idx] <- sample(available_days, 1)
      }
    }
    
    # 9. Remove or generalize time stamps
    time_cols <- c("StartedTime", "SubmittedTime", "TriggerTime")
    for (col in time_cols) {
      if (col %in% colnames(anon_participant)) {
        # Round to nearest hour for privacy
        times <- anon_participant[[col]]
        if (!all(is.na(times))) {
          # Extract hour and set minutes/seconds to 00
          rounded_times <- sapply(times, function(x) {
            if (is.na(x)) return(NA)
            hour <- as.numeric(substr(x, 1, 2))
            paste0(sprintf("%02d", hour), ":00:00")
          })
          anon_participant[[col]] <- rounded_times
        }
      }
    }
    
    anonymized_data[[participant]] <- anon_participant
  }
  
  # Combine all couples' data
  result <- bind_rows(anonymized_data)
  
  # Final step: randomize row order to prevent temporal inference
  result <- result[sample(nrow(result)), ]
  
  # Reset row names
  rownames(result) <- NULL
  
  # Subset to only columns used in the paper analyses
  paper_columns <- c(
    # Identifiers
    "ParticipantID", "CoupleID", "Role", "studyDay",
    
    # Leave/time variables  
    "isWeekend", "Leave",
    
    # Key mobility metrics from the paper
    "maxDistanceFromHomeKm", "radiusOfGyrationKm", "homeTimePercent",
    "activitySpaceAreaKm2", "locationVariance", "entropy", "maj2MinAxisRatio",
    "morningActivityMins", "afternoonActivityMins", "eveningActivityMins",
    
    # Mental health & sleep measures
    "d_epworth_sum", "SleepQuality"
  )
  
  # Keep only columns that exist in the data and are needed for analysis
  available_columns <- intersect(paper_columns, colnames(result))
  result_subset <- result[, available_columns, drop = FALSE]
  
  return(result_subset)
}

anonymized_gps <- anonymize_gps_data(d_GPS, seed = 123)

glimpse(anonymized_gps)

```


